---
title: "Inferring age mixing from transmission clusters"
author: "David Niyukuri"
date: "28 April 2019"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    code_folding: hide
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages

Load required packages for the analysis.

```{r packages}

library(dplyr)
library(ggplot2)

```

# Functions

Functions to summarise and to compute goodness of fit.

```{r functions}

# Function to summarised outputs 


# library(gmodels) # no more use of ci()

quant.med <- function(input){
  
  input <- na.omit(input)
  
  quantirles.v <- quantile(input, probs = seq(0, 1, 0.25))
  
  quantirles.25.50.75 <- as.numeric(quantirles.v)[2:4]
  
  return(quantirles.25.50.75)
  
}


min.max.sd.mean <- function(input){
  
  input <- na.omit(input)
  
  min.v <- min(input)
  max.v <- max(input)
  mean.v <- mean(input)
  sd.v <- sd(input)
  
  
  min.max.sd.mean.v <- c(min.v, max.v, mean.v, sd.v)
  
  return(min.max.sd.mean.v)
  
}


# Function for Average Root Mean Squared Error
ARMSE <- function(v1=v1, v2=v2) {
  d <- data.frame(v1,v2)
  r <- na.omit(d)
  y1 <- r[,1]
  y2 <- r[,2]
  error.na <- (y1-y2)/y2
  armse <- sqrt(mean(error.na^2)) 
  return(armse)}



# Function for Root Mean Squared Error
RMSE <- function(error) {
  error <- as.numeric(na.omit(error))
  rmse <- sqrt(mean(error^2)) 
  return(rmse)}

# Function for Mean Absolute Error
MAE <- function(error) { 
  error <- as.numeric(na.omit(error))
  mae <- mean(abs(error)) 
  return(mae)
}


# Function for Mean Realative Error
MRE <- function(error) { 
  error <- as.numeric(na.omit(error))
  mae <- mean(error) 
  return(mae)
}


```

# Read the data

Read the simulation outputs.

```{r read_data}

dr1 <- read.csv("/home/david/Desktop/Results.mcarmar.large.AD_280_777.csv")

dr <- dr1

```


# Epidemic characteristics


## Prevalence

```{r HIV_prev}

hiv.prev <- dr %>% 
  select(starts_with("prev.")) 

prev.m.15.24 <- quant.med(hiv.prev$prev.m.15.24)
prev.m.25.29 <- quant.med(hiv.prev$prev.m.25.29)
prev.m.30.34 <- quant.med(hiv.prev$prev.m.30.34)
prev.m.35.39 <- quant.med(hiv.prev$prev.m.35.39)
prev.m.40.44 <- quant.med(hiv.prev$prev.m.40.44)
prev.m.45.49 <- quant.med(hiv.prev$prev.m.45.49)

prev.w.15.24 <- quant.med(hiv.prev$prev.w.15.24)
prev.w.25.29 <- quant.med(hiv.prev$prev.w.25.29)
prev.w.30.34 <- quant.med(hiv.prev$prev.w.30.34)
prev.w.35.39 <- quant.med(hiv.prev$prev.w.35.39)
prev.w.40.44 <- quant.med(hiv.prev$prev.w.40.44)
prev.w.45.49 <- quant.med(hiv.prev$prev.w.45.49)

val.prev.F <- c(prev.m.15.24[2], prev.m.25.29[2], prev.m.30.34[2], prev.m.35.39[2], prev.m.40.44[2], prev.m.45.49[2], 
                prev.w.15.24[2], prev.w.25.29[2], prev.w.30.34[2], prev.w.35.39[2], prev.w.40.44[2], prev.w.45.49[2])

val.prev.L <- c(prev.m.15.24[1], prev.m.25.29[1], prev.m.30.34[1], prev.m.35.39[1], prev.m.40.44[1], prev.m.45.49[1], 
                prev.w.15.24[1], prev.w.25.29[1], prev.w.30.34[1], prev.w.35.39[1], prev.w.40.44[1], prev.w.45.49[1])

val.prev.U <- c(prev.m.15.24[3], prev.m.25.29[3], prev.m.30.34[3], prev.m.35.39[3], prev.m.40.44[3], prev.m.45.49[3], 
                prev.w.15.24[3], prev.w.25.29[3], prev.w.30.34[3], prev.w.35.39[3], prev.w.40.44[3], prev.w.45.49[3])


par.gender <- c(rep("men", 6), rep("women", 6))
agegroup <- rep(c("15-24", "25-29", "30-34", "35-39", "40-44", "45-49"), 2)

val.prev <- data.frame(val.prev.L, val.prev.F, val.prev.U, par.gender, agegroup)

plot.prev.men.women <- ggplot(val.prev, aes(x=agegroup, y=val.prev.F, colour=par.gender, group = par.gender)) + 
  geom_errorbar(aes(ymin=val.prev.L, ymax=val.prev.U), width=.1) +
  geom_line(size=.3) +
  geom_point() + 
  xlab("Age groups") + ylab("HIV prevalence")

plot.prev.men.women


```

## Incidence


```{r HIV_incidence}

hiv.inc <- dr %>% 
  select(starts_with("R.inc.")) 

inc.15.25.m <- quant.med(hiv.inc$R.inc.15.25.m)
inc.25.40.m <- quant.med(hiv.inc$R.inc.25.40.m)
inc.40.50.m <- quant.med(hiv.inc$R.inc.40.50.m)

inc.15.25.w <- quant.med(hiv.inc$R.inc.15.25.w)
inc.25.40.w <- quant.med(hiv.inc$R.inc.25.40.w)
inc.40.50.w <- quant.med(hiv.inc$R.inc.40.50.w)

gender <- c(rep("men", 3), rep("women", 3))
age_group <- rep(c("15-24", "25-39", "40-49"), 2)

val.inc.F <- c(inc.15.25.m[2], inc.25.40.m[2], inc.40.50.m[2],
               inc.15.25.w[2], inc.25.40.w[2], inc.40.50.w[2])
val.inc.L <- c(inc.15.25.m[1], inc.25.40.m[1], inc.40.50.m[1],
               inc.15.25.w[1], inc.25.40.w[1], inc.40.50.w[1])
val.inc.U <- c(inc.15.25.m[3], inc.25.40.m[3], inc.40.50.m[3],
               inc.15.25.w[3], inc.25.40.w[3], inc.40.50.w[3])

val.inc <- data.frame(val.inc.L, val.inc.F, val.inc.U, gender, age_group)

plot.inc.men.women <- ggplot(val.inc, aes(x=age_group, y=val.inc.F, colour=gender, group = gender)) + 
  geom_errorbar(aes(ymin=val.inc.L, ymax=val.inc.U), width=.1) +
  geom_line(size=.3) +
  geom_point() + 
  xlab("Age groups") + ylab("HIV incidence")

plot.inc.men.women


```


## Sexual behaviour



### Point prevalence of concurrent  partnerships


```{r concurrent_partners}

prev.conc.p <- dr %>% 
  select(start("R.p.prev.")) 

```

### Age mixing in partnership

#### Population level

Popultion level age mixing measurements.

```{r age_mix_rels}

dr.agemixstat <- dr %>% 
  select("R.AAD.male", "R.SDAD.male",  "R.slope.male",  "R.WSD.male", "R.BSD.male" , "R.intercept.male" )

pop.R.AAD.male <- round(quant.med(dr.agemixstat$R.AAD.male), digits = 3) 
pop.R.SDAD.male <- round(quant.med(dr.agemixstat$R.SDAD.male), digits = 3) 
pop.R.slope.male <- round(quant.med(dr.agemixstat$R.slope.male), digits = 3) 
pop.R.WSD.male <- round(quant.med(dr.agemixstat$R.WSD.male), digits = 3) 
pop.R.BSD.male <- round(quant.med(dr.agemixstat$R.BSD.male), digits = 3) 
pop.R.intercept.male <- round(quant.med(dr.agemixstat$R.intercept.male), digits = 3) 

age.mix.F <- c(pop.R.AAD.male[2], pop.R.SDAD.male[2], pop.R.BSD.male[2],
               pop.R.WSD.male[2], pop.R.slope.male[2], pop.R.intercept.male[2])

age.mix.L <- c(pop.R.AAD.male[1], pop.R.SDAD.male[1], pop.R.BSD.male[1],
               pop.R.WSD.male[1], pop.R.slope.male[1], pop.R.intercept.male[1])

age.mix.U <- c(pop.R.AAD.male[3], pop.R.SDAD.male[3], pop.R.BSD.male[3],
               pop.R.WSD.male[3], pop.R.slope.male[3], pop.R.intercept.male[3])

param.name <- c("R.AAD.male", "R.SDAD.male", "R.BSD.male" , "R.WSD.male", "R.slope.male",   "R.intercept.male" ) 

age.mixing.pop <- data.frame(param.name, age.mix.L, age.mix.F, age.mix.U)

age.mixing.pop

```



#### Sequence coverage scenarios and age mixing


Age mixing patterns (in relationships) of selected indiviuals in difference sequence coverage scenarios. These selecetd individuals are HIV positive, the measurement below assess their age mixing pattenrs withn theier sexual partnerships.

```{r age_mixng_scenarios}
# MCAR


d.MCAR <- dr %>%
  select(contains("MCAR."))


# length(names(dr1)[72:10170]) 
# 1st : "cov.MCAR.35.cl.M.15.25.F.15.25"
# last: "cov.MAR.c.95.sd.cl.size"

d.MCAR.cov.35 <- d.MCAR %>%
  select(contains("cov.MCAR.35.")) 
d.MCAR.cov.40 <- d.MCAR %>%
  select(contains("cov.MCAR.40.")) 
d.MCAR.cov.45 <- d.MCAR %>%
  select(contains("cov.MCAR.45.")) 
d.MCAR.cov.50 <- d.MCAR %>%
  select(contains("cov.MCAR.50.")) 
d.MCAR.cov.55 <- d.MCAR %>%
  select(contains("cov.MCAR.55.")) 
d.MCAR.cov.60 <- d.MCAR %>%
  select(contains("cov.MCAR.60.")) 
d.MCAR.cov.65 <- d.MCAR %>%
  select(contains("cov.MCAR.65.")) 
d.MCAR.cov.70 <- d.MCAR %>%
  select(contains("cov.MCAR.70.")) 
d.MCAR.cov.75 <- d.MCAR %>%
  select(contains("cov.MCAR.75.")) 
d.MCAR.cov.80 <- d.MCAR %>%
  select(contains("cov.MCAR.80.")) 
d.MCAR.cov.85 <- d.MCAR %>%
  select(contains("cov.MCAR.85.")) 
d.MCAR.cov.90 <- d.MCAR %>%
  select(contains("cov.MCAR.90.")) 
d.MCAR.cov.95 <- d.MCAR %>%
  select(contains("cov.MCAR.95.")) 
d.MCAR.cov.100 <- d.MCAR %>%
  select(contains("cov.MCAR.100.")) 


# Age mixing statistics in transmission networks --------------------------


# True age mix in different age mix scenarios

dr.trans.agemix.MCAR.cov.35 <- d.MCAR.cov.35 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.40 <- d.MCAR.cov.40 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.45 <- d.MCAR.cov.45 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.50 <- d.MCAR.cov.50 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.55 <- d.MCAR.cov.55 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.60 <- d.MCAR.cov.60 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.65 <- d.MCAR.cov.65 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.70 <- d.MCAR.cov.70 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.75 <- d.MCAR.cov.75 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.80 <- d.MCAR.cov.80 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.85 <- d.MCAR.cov.85 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.90 <- d.MCAR.cov.90 %>% 
  select(contains(".T."))
dr.trans.agemix.MCAR.cov.95 <- d.MCAR.cov.95 %>% 
  select(contains(".T."))


# Age mixing in transmission 

T.35.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,1]) 
T.35.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,2])
T.35.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,3])
T.35.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,4])
T.35.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,5])
T.35.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.35[,6])

T.40.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,1]) 
T.40.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,2])
T.40.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,3])
T.40.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,4])
T.40.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,5])
T.40.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.40[,6])

T.45.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,1]) 
T.45.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,2])
T.45.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,3])
T.45.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,4])
T.45.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,5])
T.45.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.45[,6])

T.50.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,1]) 
T.50.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,2])
T.50.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,3])
T.50.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,4])
T.50.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,5])
T.50.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.50[,6])

T.55.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,1]) 
T.55.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,2])
T.55.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,3])
T.55.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,4])
T.55.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,5])
T.55.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.55[,6])

T.60.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,1]) 
T.60.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,2])
T.60.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,3])
T.60.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,4])
T.60.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,5])
T.60.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.60[,6])

T.65.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,1]) 
T.65.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,2])
T.65.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,3])
T.65.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,4])
T.65.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,5])
T.65.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.65[,6])

T.70.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,1]) 
T.70.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,2])
T.70.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,3])
T.70.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,4])
T.70.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,5])
T.70.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.70[,6])

T.75.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,1]) 
T.75.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,2])
T.75.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,3])
T.75.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,4])
T.75.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,5])
T.75.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.75[,6])

T.80.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,1]) 
T.80.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,2])
T.80.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,3])
T.80.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,4])
T.80.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,5])
T.80.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.80[,6])

T.85.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,1]) 
T.85.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,2])
T.85.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,3])
T.85.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,4])
T.85.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,5])
T.85.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.85[,6])

T.90.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,1]) 
T.90.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,2])
T.90.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,3])
T.90.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,4])
T.90.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,5])
T.90.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.90[,6])

T.95.AAD.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,1]) 
T.95.SDAD.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,2])
T.95.slope.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,3])
T.95.WSD.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,4])
T.95.BSD.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,5])
T.95.intercept.male <- quant.med(dr.trans.agemix.MCAR.cov.95[,6])



age.mix.stats <- matrix(c(T.35.AAD.male[2], T.40.AAD.male[2], 
                          T.45.AAD.male[2], T.50.AAD.male[2], 
                          T.55.AAD.male[2], T.60.AAD.male[2], 
                          T.65.AAD.male[2], T.70.AAD.male[2], 
                          T.75.AAD.male[2], T.80.AAD.male[2], 
                          T.85.AAD.male[2], T.90.AAD.male[2], 
                          T.95.AAD.male[2], pop.R.AAD.male[2],
                          
                          T.35.SDAD.male[2], T.40.SDAD.male[2], 
                          T.45.SDAD.male[2], T.50.SDAD.male[2], 
                          T.55.SDAD.male[2], T.60.SDAD.male[2], 
                          T.65.SDAD.male[2], T.70.SDAD.male[2], 
                          T.75.SDAD.male[2], T.80.SDAD.male[2], 
                          T.85.SDAD.male[2], T.90.SDAD.male[2], 
                          T.95.SDAD.male[2], pop.R.SDAD.male[2],
                          
                          T.35.BSD.male[2], T.40.BSD.male[2], 
                          T.45.BSD.male[2], T.50.BSD.male[2], 
                          T.55.BSD.male[2], T.60.BSD.male[2], 
                          T.65.BSD.male[2], T.70.BSD.male[2], 
                          T.75.BSD.male[2], T.80.BSD.male[2], 
                          T.85.BSD.male[2], T.90.BSD.male[2], 
                          T.95.BSD.male[2], pop.R.BSD.male[2],
                          
                          T.35.WSD.male[2], T.40.WSD.male[2], 
                          T.45.WSD.male[2], T.50.WSD.male[2], 
                          T.55.WSD.male[2], T.60.WSD.male[2], 
                          T.65.WSD.male[2], T.70.WSD.male[2], 
                          T.75.WSD.male[2], T.80.WSD.male[2], 
                          T.85.WSD.male[2], T.90.WSD.male[2], 
                          T.95.WSD.male[2], pop.R.WSD.male[2],
                          
                          T.35.slope.male[2], T.40.slope.male[2], 
                          T.45.slope.male[2], T.50.slope.male[2], 
                          T.55.slope.male[2], T.60.slope.male[2], 
                          T.65.slope.male[2], T.70.slope.male[2], 
                          T.75.slope.male[2], T.80.slope.male[2], 
                          T.85.slope.male[2], T.90.slope.male[2], 
                          T.95.slope.male[2], pop.R.slope.male[2],
                          
                          T.35.intercept.male[2], T.40.intercept.male[2], 
                          T.45.intercept.male[2], T.50.intercept.male[2], 
                          T.55.intercept.male[2], T.60.intercept.male[2], 
                          T.65.intercept.male[2], T.70.intercept.male[2], 
                          T.75.intercept.male[2], T.80.intercept.male[2], 
                          T.85.intercept.male[2], T.90.intercept.male[2], 
                          T.95.intercept.male[2], pop.R.intercept.male[2]
),

ncol = 14,
byrow = TRUE)

age.mix.stats <- round(age.mix.stats, digits = 2)

colnames(age.mix.stats) <- c("cov.35", "cov.40", "cov.45",
                             "cov.50", "cov.55", "cov.60",
                             "cov.65", "cov.70", "cov.75",
                             "cov.80", "cov.85", "cov.90",
                             "cov.95", "pop.lev")

rownames(age.mix.stats) <- c("AAD.male", "SDAD.male", "BSD.male",  "WSD.male", "slope.male", "intercept.male") 

age.mix.stats


````

#### Difference between true values and values at different sampling scenarios in MCAR

```{r age_mixing_diff}

d.AAD.male <- (age.mix.stats[1,14] - age.mix.stats[1,])/age.mix.stats[1,14]
d.SDAD.male <- (age.mix.stats[2,14] - age.mix.stats[2,])/age.mix.stats[2,14]
d.slope.male <- (age.mix.stats[3,14] - age.mix.stats[3,])/age.mix.stats[3,14]
d.WSD.male <- (age.mix.stats[4,14] - age.mix.stats[4,])/age.mix.stats[4,14]
d.BSD.male <- (age.mix.stats[5,14] - age.mix.stats[5,])/age.mix.stats[5,14]
d.interc.male <- (age.mix.stats[6,14] - age.mix.stats[6,])/age.mix.stats[6,14]

diff.cov.true.age.mix.stats <- matrix(c(d.AAD.male, d.SDAD.male, d.BSD.male,
                                        d.WSD.male, d.slope.male, d.interc.male),
                                      ncol = 14,
                                      byrow = TRUE)

colnames(diff.cov.true.age.mix.stats) <- c("cov.35", "cov.40", "cov.45",
                                           "cov.50", "cov.55", "cov.60",
                                           "cov.65", "cov.70", "cov.75",
                                           "cov.80", "cov.85", "cov.90",
                                           "cov.95", "pop.lev")

rownames(diff.cov.true.age.mix.stats) <- c("d.AAD.male", "d.SDAD.male", "d.BSD.male", "d.WSD.male", "d.slope.male",   "d.intercept.male") 



error.age.mix.AAD.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                     
                                     F = c(as.numeric(diff.cov.true.age.mix.stats[1,])))
error.age.mix.AAD.male$parameter <- "AAD.male"

error.age.mix.SDAD.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                      
                                      F = c(as.numeric(diff.cov.true.age.mix.stats[2,])))
error.age.mix.SDAD.male$parameter <- "SDAD.male"


error.age.mix.slope.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                       
                                       F = c(as.numeric(diff.cov.true.age.mix.stats[3,])))
error.age.mix.slope.male$parameter <- "slope.male"

error.age.mix.WSD.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                     
                                     F = c(as.numeric(diff.cov.true.age.mix.stats[4,])))
error.age.mix.WSD.male$parameter <- "WSD.male"


error.age.mix.BSD.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                     
                                     F = c(as.numeric(diff.cov.true.age.mix.stats[5,])))
error.age.mix.BSD.male$parameter <- "BSD.male"


error.age.mix.intercept.male <- data.frame(x=c(seq(from=35, to=95, by=5), "pop"),
                                           
                                           F = c(as.numeric(diff.cov.true.age.mix.stats[6,])))
error.age.mix.intercept.male$parameter <- "intercept.male"


errors.age.mixing <- rbind(error.age.mix.AAD.male, error.age.mix.BSD.male,
                           error.age.mix.SDAD.male,error.age.mix.WSD.male,
                           error.age.mix.intercept.male, error.age.mix.slope.male)


plots.errors.age.mix  <- ggplot(errors.age.mixing, aes(x=x, y=F, colour=parameter, group = parameter)) + 
  # geom_errorbar(aes(ymin=L, ymax=U), width=.1) +
  geom_line(size=.3) +
  geom_point() + 
  xlab("Sequence coverage") + ylab("Error") 

plots.errors.age.mix

```


# Transmission clusters

## Statistics of size of transmission clusters

Mean, median, and standard deviation of transmission clusters.

```{r transm_clusters}

# Cluster sizes

dr.cl.size.MCAR.cov.35 <- d.MCAR.cov.35 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.40 <- d.MCAR.cov.40 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.45 <- d.MCAR.cov.45 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.50 <- d.MCAR.cov.50 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.55 <- d.MCAR.cov.55 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.60 <- d.MCAR.cov.60 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.65 <- d.MCAR.cov.65 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.70 <- d.MCAR.cov.70 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.75 <- d.MCAR.cov.75 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.80 <- d.MCAR.cov.80 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.85 <- d.MCAR.cov.85 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.90 <- d.MCAR.cov.90 %>% 
  select(contains("cl.size"))
dr.cl.size.MCAR.cov.95 <- d.MCAR.cov.95 %>% 
  select(contains("cl.size"))

dr.cl.size.MCAR.cov.100 <- d.MCAR.cov.100 %>% 
  select(contains("cl.size"))


cl.size.mean.35 <- quant.med(dr.cl.size.MCAR.cov.35$cov.MCAR.35.mean.cl.size)
cl.size.med.35 <- quant.med(dr.cl.size.MCAR.cov.35$cov.MCAR.35.med.cl.size)
cl.size.sd.35 <- quant.med(dr.cl.size.MCAR.cov.35$cov.MCAR.35.sd.cl.size)

cl.size.mean.40 <- quant.med(dr.cl.size.MCAR.cov.40$cov.MCAR.40.mean.cl.size)
cl.size.med.40 <- quant.med(dr.cl.size.MCAR.cov.40$cov.MCAR.40.med.cl.size)
cl.size.sd.40 <- quant.med(dr.cl.size.MCAR.cov.40$cov.MCAR.40.sd.cl.size)

cl.size.mean.45 <- quant.med(dr.cl.size.MCAR.cov.45$cov.MCAR.45.mean.cl.size)
cl.size.med.45 <- quant.med(dr.cl.size.MCAR.cov.45$cov.MCAR.45.med.cl.size)
cl.size.sd.45 <- quant.med(dr.cl.size.MCAR.cov.45$cov.MCAR.45.sd.cl.size)

cl.size.mean.50 <- quant.med(dr.cl.size.MCAR.cov.50$cov.MCAR.50.mean.cl.size)
cl.size.med.50 <- quant.med(dr.cl.size.MCAR.cov.50$cov.MCAR.50.med.cl.size)
cl.size.sd.50 <- quant.med(dr.cl.size.MCAR.cov.50$cov.MCAR.50.sd.cl.size)

cl.size.mean.55 <- quant.med(dr.cl.size.MCAR.cov.55$cov.MCAR.55.mean.cl.size)
cl.size.med.55 <- quant.med(dr.cl.size.MCAR.cov.55$cov.MCAR.55.med.cl.size)
cl.size.sd.55 <- quant.med(dr.cl.size.MCAR.cov.55$cov.MCAR.55.sd.cl.size)

cl.size.mean.60 <- quant.med(dr.cl.size.MCAR.cov.60$cov.MCAR.60.mean.cl.size)
cl.size.med.60 <- quant.med(dr.cl.size.MCAR.cov.60$cov.MCAR.60.med.cl.size)
cl.size.sd.60 <- quant.med(dr.cl.size.MCAR.cov.60$cov.MCAR.60.sd.cl.size)

cl.size.mean.65 <- quant.med(dr.cl.size.MCAR.cov.65$cov.MCAR.65.mean.cl.size)
cl.size.med.65 <- quant.med(dr.cl.size.MCAR.cov.65$cov.MCAR.65.med.cl.size)
cl.size.sd.65 <- quant.med(dr.cl.size.MCAR.cov.65$cov.MCAR.65.sd.cl.size)

cl.size.mean.70 <- quant.med(dr.cl.size.MCAR.cov.70$cov.MCAR.70.mean.cl.size)
cl.size.med.70 <- quant.med(dr.cl.size.MCAR.cov.70$cov.MCAR.70.med.cl.size)
cl.size.sd.70 <- quant.med(dr.cl.size.MCAR.cov.70$cov.MCAR.70.sd.cl.size)

cl.size.mean.75 <- quant.med(dr.cl.size.MCAR.cov.75$cov.MCAR.75.mean.cl.size)
cl.size.med.75 <- quant.med(dr.cl.size.MCAR.cov.75$cov.MCAR.75.med.cl.size)
cl.size.sd.75 <- quant.med(dr.cl.size.MCAR.cov.75$cov.MCAR.75.sd.cl.size)

cl.size.mean.80 <- quant.med(dr.cl.size.MCAR.cov.80$cov.MCAR.80.mean.cl.size)
cl.size.med.80 <- quant.med(dr.cl.size.MCAR.cov.80$cov.MCAR.80.med.cl.size)
cl.size.sd.80 <- quant.med(dr.cl.size.MCAR.cov.80$cov.MCAR.80.sd.cl.size)

cl.size.mean.85 <- quant.med(dr.cl.size.MCAR.cov.85$cov.MCAR.85.mean.cl.size)
cl.size.med.85 <- quant.med(dr.cl.size.MCAR.cov.85$cov.MCAR.85.med.cl.size)
cl.size.sd.85 <- quant.med(dr.cl.size.MCAR.cov.85$cov.MCAR.85.sd.cl.size)

cl.size.mean.90 <- quant.med(dr.cl.size.MCAR.cov.90$cov.MCAR.90.mean.cl.size)
cl.size.med.90 <- quant.med(dr.cl.size.MCAR.cov.90$cov.MCAR.90.med.cl.size)
cl.size.sd.90 <- quant.med(dr.cl.size.MCAR.cov.90$cov.MCAR.90.sd.cl.size)

cl.size.mean.95 <- quant.med(dr.cl.size.MCAR.cov.95$cov.MCAR.95.mean.cl.size)
cl.size.med.95 <- quant.med(dr.cl.size.MCAR.cov.95$cov.MCAR.95.med.cl.size)
cl.size.sd.95 <- quant.med(dr.cl.size.MCAR.cov.95$cov.MCAR.95.sd.cl.size)


cl.size.mean.100 <- quant.med(dr.cl.size.MCAR.cov.100$cov.MCAR.100.mean.cl.size)
cl.size.med.100 <- quant.med(dr.cl.size.MCAR.cov.100$cov.MCAR.100.med.cl.size)
cl.size.sd.100 <- quant.med(dr.cl.size.MCAR.cov.100$cov.MCAR.100.sd.cl.size)


cl.size.mean.df <- data.frame(x=c("cov.35", "cov.40", "cov.45",
                                  "cov.50", "cov.55", "cov.60",
                                  "cov.65", "cov.70", "cov.75",
                                  "cov.80", "cov.85", "cov.90",
                                  "cov.95", "cov.100"),
                              
                              F = c(cl.size.mean.35[2], cl.size.mean.40[2], 
                                    cl.size.mean.45[2], cl.size.mean.50[2], 
                                    cl.size.mean.55[2], cl.size.mean.60[2], 
                                    cl.size.mean.65[2], cl.size.mean.70[2], 
                                    cl.size.mean.75[2], cl.size.mean.80[2], 
                                    cl.size.mean.85[2], cl.size.mean.90[2], 
                                    cl.size.mean.95[2], cl.size.mean.100[2]),
                              
                              L = c(cl.size.mean.35[1], cl.size.mean.40[1], 
                                    cl.size.mean.45[1], cl.size.mean.50[1], 
                                    cl.size.mean.55[1], cl.size.mean.60[1], 
                                    cl.size.mean.65[1], cl.size.mean.70[1], 
                                    cl.size.mean.75[1], cl.size.mean.80[1], 
                                    cl.size.mean.85[1], cl.size.mean.90[1], 
                                    cl.size.mean.95[1], cl.size.mean.100[1]),
                              
                              U = c(cl.size.mean.35[3], cl.size.mean.40[3], 
                                    cl.size.mean.45[3], cl.size.mean.50[3], 
                                    cl.size.mean.55[3], cl.size.mean.60[3], 
                                    cl.size.mean.65[3], cl.size.mean.70[3], 
                                    cl.size.mean.75[3], cl.size.mean.80[3], 
                                    cl.size.mean.85[3], cl.size.mean.90[3], 
                                    cl.size.mean.95[3], cl.size.mean.100[3]))

cl.size.mean.df$param <- "mean"


cl.size.med.df <- data.frame(x=c("cov.35", "cov.40", "cov.45",
                                 "cov.50", "cov.55", "cov.60",
                                 "cov.65", "cov.70", "cov.75",
                                 "cov.80", "cov.85", "cov.90",
                                 "cov.95", "cov.100"),
                             
                             F = c(cl.size.med.35[2], cl.size.med.40[2], 
                                   cl.size.med.45[2], cl.size.med.50[2], 
                                   cl.size.med.55[2], cl.size.med.60[2], 
                                   cl.size.med.65[2], cl.size.med.70[2], 
                                   cl.size.med.75[2], cl.size.med.80[2], 
                                   cl.size.med.85[2], cl.size.med.90[2], 
                                   cl.size.med.95[2], cl.size.med.100[2]),
                             
                             L = c(cl.size.med.35[1], cl.size.med.40[1], 
                                   cl.size.med.45[1], cl.size.med.50[1], 
                                   cl.size.med.55[1], cl.size.med.60[1], 
                                   cl.size.med.65[1], cl.size.med.70[1], 
                                   cl.size.med.75[1], cl.size.med.80[1], 
                                   cl.size.med.85[1], cl.size.med.90[1], 
                                   cl.size.med.95[1], cl.size.med.100[1]),
                             
                             U = c(cl.size.med.35[3], cl.size.med.40[3], 
                                   cl.size.med.45[3], cl.size.med.50[3], 
                                   cl.size.med.55[3], cl.size.med.60[3], 
                                   cl.size.med.65[3], cl.size.med.70[3], 
                                   cl.size.med.75[3], cl.size.med.80[3], 
                                   cl.size.med.85[3], cl.size.med.90[3], 
                                   cl.size.med.95[3], cl.size.med.100[3]))

cl.size.med.df$param <- "med"


cl.size.sd.df <- data.frame(x=c("cov.35", "cov.40", "cov.45",
                                "cov.50", "cov.55", "cov.60",
                                "cov.65", "cov.70", "cov.75",
                                "cov.80", "cov.85", "cov.90",
                                "cov.95", "cov.100"),
                            
                            F = c(cl.size.sd.35[2], cl.size.sd.40[2], 
                                  cl.size.sd.45[2], cl.size.sd.50[2], 
                                  cl.size.sd.55[2], cl.size.sd.60[2], 
                                  cl.size.sd.65[2], cl.size.sd.70[2], 
                                  cl.size.sd.75[2], cl.size.sd.80[2], 
                                  cl.size.sd.85[2], cl.size.sd.90[2], 
                                  cl.size.sd.95[2], cl.size.sd.100[2]),
                            
                            L = c(cl.size.sd.35[1], cl.size.sd.40[1], 
                                  cl.size.sd.45[1], cl.size.sd.50[1], 
                                  cl.size.sd.55[1], cl.size.sd.60[1], 
                                  cl.size.sd.65[1], cl.size.sd.70[1], 
                                  cl.size.sd.75[1], cl.size.sd.80[1], 
                                  cl.size.sd.85[1], cl.size.sd.90[1], 
                                  cl.size.sd.95[1], cl.size.sd.100[1]),
                            
                            U = c(cl.size.sd.35[3], cl.size.sd.40[3], 
                                  cl.size.sd.45[3], cl.size.sd.50[3], 
                                  cl.size.sd.55[3], cl.size.sd.60[3], 
                                  cl.size.sd.65[3], cl.size.sd.70[3], 
                                  cl.size.sd.75[3], cl.size.sd.80[3], 
                                  cl.size.sd.85[3], cl.size.sd.90[3], 
                                  cl.size.sd.95[3], cl.size.sd.100[3]))

cl.size.sd.df$param <- "sd"


clust.size.stats <- rbind(cl.size.mean.df, cl.size.med.df, cl.size.sd.df)


plot.clust.size.stats <- ggplot(clust.size.stats, aes(x=x, y=F, colour=param, group = param)) + 
  geom_errorbar(aes(ymin=L, ymax=U), width=.1) +
  geom_line(size=.3) +
  geom_point() + 
  xlab("Sample size") + ylab("Value")
# ggtitle("Statistics  of transmission clusters")


plot.clust.size.stats


```



# Number of pairings in transmission clusters


## True pairings at 100% coverage

```{r pairings_100}

dr.cov.100 <- dr %>% 
  select(contains(".100"))

M.15.25.F.15.25.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.15.25.F.15.25) # quant.med(dr.cov.100$cov.100.M.15.25.F.15.25)
M.25.40.F.15.25.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.25.40.F.15.25) # quant.med(dr.cov.100$cov.100.M.25.40.F.15.25)
M.40.50.F.15.25.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.40.50.F.15.25) # quant.med(dr.cov.100$cov.100.M.40.50.F.15.25)

M.15.25.F.25.40.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.15.25.F.25.40) # quant.med(dr.cov.100$cov.100.M.15.25.F.25.40)
M.25.40.F.25.40.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.25.40.F.25.40) # quant.med(dr.cov.100$cov.100.M.25.40.F.25.40)
M.40.50.F.25.40.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.40.50.F.25.40) # quant.med(dr.cov.100$cov.100.M.40.50.F.25.40)

M.15.25.F.40.50.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.15.25.F.40.50) # quant.med(dr.cov.100$cov.100.M.15.25.F.40.50)
M.25.40.F.40.50.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.25.40.F.40.50) # quant.med(dr.cov.100$cov.100.M.25.40.F.40.50)
M.40.50.F.40.50.cov.100 <- quant.med(dr.cov.100$cov.MCAR.100.cl.true.M.40.50.F.40.50) # quant.med(dr.cov.100$cov.100.M.40.50.F.40.50)



cov.100.age.groups.table <- matrix(c((M.15.25.F.15.25.cov.100[2]), (M.15.25.F.25.40.cov.100[2]), (M.15.25.F.40.50.cov.100[2]),
                                     (M.25.40.F.15.25.cov.100[2]), (M.25.40.F.25.40.cov.100[2]), (M.25.40.F.40.50.cov.100[2]),
                                     (M.40.50.F.15.25.cov.100[2]), (M.40.50.F.25.40.cov.100[2]), (M.40.50.F.40.50.cov.100[2])),
                                   ncol = 3,
                                   byrow = TRUE)

colnames(cov.100.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(cov.100.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

cov.100.age.groups.table

```


## True pairings at different sequence coverage scenarios


```{r pairing_true_scen}

# Cov 35

M.15.25.F.15.25.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.true.M.40.50.F.40.50)


# Cov 40

M.15.25.F.15.25.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.true.M.40.50.F.40.50)

# Cov 45


M.15.25.F.15.25.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.true.M.40.50.F.40.50)


# Cov 50


M.15.25.F.15.25.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.true.M.40.50.F.40.50)


# Cov 55


M.15.25.F.15.25.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.true.M.40.50.F.40.50)


# Cov 60


M.15.25.F.15.25.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.true.M.40.50.F.40.50)


# Cov 65


M.15.25.F.15.25.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.true.M.40.50.F.40.50)

# Cov 70


M.15.25.F.15.25.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.true.M.40.50.F.40.50)


# Cov 75


M.15.25.F.15.25.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.true.M.40.50.F.40.50)


# Cov 80


M.15.25.F.15.25.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.true.M.40.50.F.40.50)


# Cov 85


M.15.25.F.15.25.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.true.M.40.50.F.40.50)

# Cov 90


M.15.25.F.15.25.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.true.M.40.50.F.40.50)


# Cov 95


M.15.25.F.15.25.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.true.M.40.50.F.40.50)



# Agregated table of pairings: true 


agreggated.pairings.mat <- matrix(c(M.15.25.F.15.25.MCAR.cov.35[2], M.15.25.F.15.25.MCAR.cov.40[2], 
                                    M.15.25.F.15.25.MCAR.cov.45[2], M.15.25.F.15.25.MCAR.cov.50[2], 
                                    M.15.25.F.15.25.MCAR.cov.55[2], M.15.25.F.15.25.MCAR.cov.60[2], 
                                    M.15.25.F.15.25.MCAR.cov.65[2], M.15.25.F.15.25.MCAR.cov.70[2], 
                                    M.15.25.F.15.25.MCAR.cov.75[2], M.15.25.F.15.25.MCAR.cov.80[2], 
                                    M.15.25.F.15.25.MCAR.cov.85[2], M.15.25.F.15.25.MCAR.cov.90[2], 
                                    M.15.25.F.15.25.MCAR.cov.95[2], M.15.25.F.15.25.cov.100[2],
                                    
                                    M.25.40.F.15.25.MCAR.cov.35[2], M.25.40.F.15.25.MCAR.cov.40[2], 
                                    M.25.40.F.15.25.MCAR.cov.45[2], M.25.40.F.15.25.MCAR.cov.50[2], 
                                    M.25.40.F.15.25.MCAR.cov.55[2], M.25.40.F.15.25.MCAR.cov.60[2], 
                                    M.25.40.F.15.25.MCAR.cov.65[2], M.25.40.F.15.25.MCAR.cov.70[2], 
                                    M.25.40.F.15.25.MCAR.cov.75[2], M.25.40.F.15.25.MCAR.cov.80[2], 
                                    M.25.40.F.15.25.MCAR.cov.85[2], M.25.40.F.15.25.MCAR.cov.90[2], 
                                    M.25.40.F.15.25.MCAR.cov.95[2], M.25.40.F.15.25.cov.100[2],
                                    
                                    M.40.50.F.15.25.MCAR.cov.35[2], M.40.50.F.15.25.MCAR.cov.40[2], 
                                    M.40.50.F.15.25.MCAR.cov.45[2], M.40.50.F.15.25.MCAR.cov.50[2], 
                                    M.40.50.F.15.25.MCAR.cov.55[2], M.40.50.F.15.25.MCAR.cov.60[2], 
                                    M.40.50.F.15.25.MCAR.cov.65[2], M.40.50.F.15.25.MCAR.cov.70[2], 
                                    M.40.50.F.15.25.MCAR.cov.75[2], M.40.50.F.15.25.MCAR.cov.80[2], 
                                    M.40.50.F.15.25.MCAR.cov.85[2], M.40.50.F.15.25.MCAR.cov.90[2], 
                                    M.40.50.F.15.25.MCAR.cov.95[2], M.40.50.F.15.25.cov.100[2],
                                    
                                    M.15.25.F.25.40.MCAR.cov.35[2], M.15.25.F.25.40.MCAR.cov.40[2], 
                                    M.15.25.F.25.40.MCAR.cov.45[2], M.15.25.F.25.40.MCAR.cov.50[2], 
                                    M.15.25.F.25.40.MCAR.cov.55[2], M.15.25.F.25.40.MCAR.cov.60[2], 
                                    M.15.25.F.25.40.MCAR.cov.65[2], M.15.25.F.25.40.MCAR.cov.70[2], 
                                    M.15.25.F.25.40.MCAR.cov.75[2], M.15.25.F.25.40.MCAR.cov.80[2], 
                                    M.15.25.F.25.40.MCAR.cov.85[2], M.15.25.F.25.40.MCAR.cov.90[2], 
                                    M.15.25.F.25.40.MCAR.cov.95[2], M.15.25.F.25.40.cov.100[2],
                                    
                                    M.25.40.F.25.40.MCAR.cov.35[2], M.25.40.F.25.40.MCAR.cov.40[2], 
                                    M.25.40.F.25.40.MCAR.cov.45[2], M.25.40.F.25.40.MCAR.cov.50[2], 
                                    M.25.40.F.25.40.MCAR.cov.55[2], M.25.40.F.25.40.MCAR.cov.60[2], 
                                    M.25.40.F.25.40.MCAR.cov.65[2], M.25.40.F.25.40.MCAR.cov.70[2], 
                                    M.25.40.F.25.40.MCAR.cov.75[2], M.25.40.F.25.40.MCAR.cov.80[2], 
                                    M.25.40.F.25.40.MCAR.cov.85[2], M.25.40.F.25.40.MCAR.cov.90[2], 
                                    M.25.40.F.25.40.MCAR.cov.95[2], M.25.40.F.25.40.cov.100[2],
                                    
                                    M.40.50.F.25.40.MCAR.cov.35[2], M.40.50.F.25.40.MCAR.cov.40[2], 
                                    M.40.50.F.25.40.MCAR.cov.45[2], M.40.50.F.25.40.MCAR.cov.50[2], 
                                    M.40.50.F.25.40.MCAR.cov.55[2], M.40.50.F.25.40.MCAR.cov.60[2], 
                                    M.40.50.F.25.40.MCAR.cov.65[2], M.40.50.F.25.40.MCAR.cov.70[2], 
                                    M.40.50.F.25.40.MCAR.cov.75[2], M.40.50.F.25.40.MCAR.cov.80[2], 
                                    M.40.50.F.25.40.MCAR.cov.85[2], M.40.50.F.25.40.MCAR.cov.90[2], 
                                    M.40.50.F.25.40.MCAR.cov.95[2], M.40.50.F.25.40.cov.100[2],
                                    
                                    M.15.25.F.40.50.MCAR.cov.35[2], M.15.25.F.40.50.MCAR.cov.40[2], 
                                    M.15.25.F.40.50.MCAR.cov.45[2], M.15.25.F.40.50.MCAR.cov.50[2], 
                                    M.15.25.F.40.50.MCAR.cov.55[2], M.15.25.F.40.50.MCAR.cov.60[2], 
                                    M.15.25.F.40.50.MCAR.cov.65[2], M.15.25.F.40.50.MCAR.cov.70[2], 
                                    M.15.25.F.40.50.MCAR.cov.75[2], M.15.25.F.40.50.MCAR.cov.80[2], 
                                    M.15.25.F.40.50.MCAR.cov.85[2], M.15.25.F.40.50.MCAR.cov.90[2], 
                                    M.15.25.F.40.50.MCAR.cov.95[2], M.15.25.F.40.50.cov.100[2],
                                    
                                    M.25.40.F.40.50.MCAR.cov.35[2], M.25.40.F.40.50.MCAR.cov.40[2], 
                                    M.25.40.F.40.50.MCAR.cov.45[2], M.25.40.F.40.50.MCAR.cov.50[2], 
                                    M.25.40.F.40.50.MCAR.cov.55[2], M.25.40.F.40.50.MCAR.cov.60[2], 
                                    M.25.40.F.40.50.MCAR.cov.65[2], M.25.40.F.40.50.MCAR.cov.70[2], 
                                    M.25.40.F.40.50.MCAR.cov.75[2], M.25.40.F.40.50.MCAR.cov.80[2], 
                                    M.25.40.F.40.50.MCAR.cov.85[2], M.25.40.F.40.50.MCAR.cov.90[2], 
                                    M.25.40.F.40.50.MCAR.cov.95[2], M.25.40.F.40.50.cov.100[2],
                                    
                                    M.40.50.F.40.50.MCAR.cov.35[2], M.40.50.F.40.50.MCAR.cov.40[2], 
                                    M.40.50.F.40.50.MCAR.cov.45[2], M.40.50.F.40.50.MCAR.cov.50[2], 
                                    M.40.50.F.40.50.MCAR.cov.55[2], M.40.50.F.40.50.MCAR.cov.60[2], 
                                    M.40.50.F.40.50.MCAR.cov.65[2], M.40.50.F.40.50.MCAR.cov.70[2], 
                                    M.40.50.F.40.50.MCAR.cov.75[2], M.40.50.F.40.50.MCAR.cov.80[2], 
                                    M.40.50.F.40.50.MCAR.cov.85[2], M.40.50.F.40.50.MCAR.cov.90[2], 
                                    M.40.50.F.40.50.MCAR.cov.95[2], M.40.50.F.40.50.cov.100[2]),
                                  
                                  ncol = 14,
                                  byrow = TRUE)

colnames(agreggated.pairings.mat) <- c("Cov.35", "Cov.40", "Cov.45",
                                       "Cov.50", "Cov.55", "Cov.60",
                                       "Cov.65", "Cov.70", "Cov.75",
                                       "Cov.80", "Cov.85", "Cov.90",
                                       "Cov.95", "Cov.100")

rownames(agreggated.pairings.mat) <- c("M.15.25.F.15.25", "M.25.40.F.15.25", "M.40.50.F.15.25",
                                       "M.15.25.F.25.40", "M.25.40.F.25.40", "M.40.50.F.25.40",
                                       "M.15.25.F.40.50", "M.25.40.F.40.50", "M.40.50.F.40.50")
agreggated.pairings.mat

```



## Pairings  inferred from transmission clusters

```{r pairing_clust_inf}


# Cov 35

M.15.25.F.15.25.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.35 <- quant.med(d.MCAR.cov.35$cov.MCAR.35.cl.M.40.50.F.40.50)



MCAR.cov.35.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.35[2]), (M.15.25.F.25.40.MCAR.cov.cl.35[2]), (M.15.25.F.40.50.MCAR.cov.cl.35[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.35[2]), (M.25.40.F.25.40.MCAR.cov.cl.35[2]), (M.25.40.F.40.50.MCAR.cov.cl.35[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.35[2]), (M.40.50.F.25.40.MCAR.cov.cl.35[2]), (M.40.50.F.40.50.MCAR.cov.cl.35[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.35.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.35.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")



# Cov 40

M.15.25.F.15.25.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.40 <- quant.med(d.MCAR.cov.40$cov.MCAR.40.cl.M.40.50.F.40.50)



MCAR.cov.40.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.40[2]), (M.15.25.F.25.40.MCAR.cov.cl.40[2]), (M.15.25.F.40.50.MCAR.cov.cl.40[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.40[2]), (M.25.40.F.25.40.MCAR.cov.cl.40[2]), (M.25.40.F.40.50.MCAR.cov.cl.40[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.40[2]), (M.40.50.F.25.40.MCAR.cov.cl.40[2]), (M.40.50.F.40.50.MCAR.cov.cl.40[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.40.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.40.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")



# Cov 45

M.15.25.F.15.25.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.45 <- quant.med(d.MCAR.cov.45$cov.MCAR.45.cl.M.40.50.F.40.50)



MCAR.cov.45.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.45[2]), (M.15.25.F.25.40.MCAR.cov.cl.45[2]), (M.15.25.F.40.50.MCAR.cov.cl.45[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.45[2]), (M.25.40.F.25.40.MCAR.cov.cl.45[2]), (M.25.40.F.40.50.MCAR.cov.cl.45[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.45[2]), (M.40.50.F.25.40.MCAR.cov.cl.45[2]), (M.40.50.F.40.50.MCAR.cov.cl.45[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.45.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.45.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 50

M.15.25.F.15.25.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.50 <- quant.med(d.MCAR.cov.50$cov.MCAR.50.cl.M.40.50.F.40.50)



MCAR.cov.50.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.50[2]), (M.15.25.F.25.40.MCAR.cov.cl.50[2]), (M.15.25.F.40.50.MCAR.cov.cl.50[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.50[2]), (M.25.40.F.25.40.MCAR.cov.cl.50[2]), (M.25.40.F.40.50.MCAR.cov.cl.50[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.50[2]), (M.40.50.F.25.40.MCAR.cov.cl.50[2]), (M.40.50.F.40.50.MCAR.cov.cl.50[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.50.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.50.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")


# Cov 55

M.15.25.F.15.25.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.55 <- quant.med(d.MCAR.cov.55$cov.MCAR.55.cl.M.40.50.F.40.50)



MCAR.cov.55.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.55[2]), (M.15.25.F.25.40.MCAR.cov.cl.55[2]), (M.15.25.F.40.50.MCAR.cov.cl.55[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.55[2]), (M.25.40.F.25.40.MCAR.cov.cl.55[2]), (M.25.40.F.40.50.MCAR.cov.cl.55[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.55[2]), (M.40.50.F.25.40.MCAR.cov.cl.55[2]), (M.40.50.F.40.50.MCAR.cov.cl.55[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.55.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.55.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 60

M.15.25.F.15.25.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.60 <- quant.med(d.MCAR.cov.60$cov.MCAR.60.cl.M.40.50.F.40.50)



MCAR.cov.60.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.60[2]), (M.15.25.F.25.40.MCAR.cov.cl.60[2]), (M.15.25.F.40.50.MCAR.cov.cl.60[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.60[2]), (M.25.40.F.25.40.MCAR.cov.cl.60[2]), (M.25.40.F.40.50.MCAR.cov.cl.60[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.60[2]), (M.40.50.F.25.40.MCAR.cov.cl.60[2]), (M.40.50.F.40.50.MCAR.cov.cl.60[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.60.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.60.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")


# Cov 65

M.15.25.F.15.25.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.65 <- quant.med(d.MCAR.cov.65$cov.MCAR.65.cl.M.40.50.F.40.50)



MCAR.cov.65.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.65[2]), (M.15.25.F.25.40.MCAR.cov.cl.65[2]), (M.15.25.F.40.50.MCAR.cov.cl.65[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.65[2]), (M.25.40.F.25.40.MCAR.cov.cl.65[2]), (M.25.40.F.40.50.MCAR.cov.cl.65[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.65[2]), (M.40.50.F.25.40.MCAR.cov.cl.65[2]), (M.40.50.F.40.50.MCAR.cov.cl.65[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.65.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.65.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 70

M.15.25.F.15.25.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.70 <- quant.med(d.MCAR.cov.70$cov.MCAR.70.cl.M.40.50.F.40.50)



MCAR.cov.70.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.70[2]), (M.15.25.F.25.40.MCAR.cov.cl.70[2]), (M.15.25.F.40.50.MCAR.cov.cl.70[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.70[2]), (M.25.40.F.25.40.MCAR.cov.cl.70[2]), (M.25.40.F.40.50.MCAR.cov.cl.70[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.70[2]), (M.40.50.F.25.40.MCAR.cov.cl.70[2]), (M.40.50.F.40.50.MCAR.cov.cl.70[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.70.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.70.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 75

M.15.25.F.15.25.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.75 <- quant.med(d.MCAR.cov.75$cov.MCAR.75.cl.M.40.50.F.40.50)



MCAR.cov.75.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.75[2]), (M.15.25.F.25.40.MCAR.cov.cl.75[2]), (M.15.25.F.40.50.MCAR.cov.cl.75[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.75[2]), (M.25.40.F.25.40.MCAR.cov.cl.75[2]), (M.25.40.F.40.50.MCAR.cov.cl.75[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.75[2]), (M.40.50.F.25.40.MCAR.cov.cl.75[2]), (M.40.50.F.40.50.MCAR.cov.cl.75[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.75.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.75.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")


# Cov 80

M.15.25.F.15.25.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.80 <- quant.med(d.MCAR.cov.80$cov.MCAR.80.cl.M.40.50.F.40.50)



MCAR.cov.80.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.80[2]), (M.15.25.F.25.40.MCAR.cov.cl.80[2]), (M.15.25.F.40.50.MCAR.cov.cl.80[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.80[2]), (M.25.40.F.25.40.MCAR.cov.cl.80[2]), (M.25.40.F.40.50.MCAR.cov.cl.80[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.80[2]), (M.40.50.F.25.40.MCAR.cov.cl.80[2]), (M.40.50.F.40.50.MCAR.cov.cl.80[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.80.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.80.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")


# Cov 85

M.15.25.F.15.25.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.85 <- quant.med(d.MCAR.cov.85$cov.MCAR.85.cl.M.40.50.F.40.50)



MCAR.cov.85.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.85[2]), (M.15.25.F.25.40.MCAR.cov.cl.85[2]), (M.15.25.F.40.50.MCAR.cov.cl.85[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.85[2]), (M.25.40.F.25.40.MCAR.cov.cl.85[2]), (M.25.40.F.40.50.MCAR.cov.cl.85[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.85[2]), (M.40.50.F.25.40.MCAR.cov.cl.85[2]), (M.40.50.F.40.50.MCAR.cov.cl.85[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.85.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.85.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 90

M.15.25.F.15.25.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.90 <- quant.med(d.MCAR.cov.90$cov.MCAR.90.cl.M.40.50.F.40.50)



MCAR.cov.90.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.90[2]), (M.15.25.F.25.40.MCAR.cov.cl.90[2]), (M.15.25.F.40.50.MCAR.cov.cl.90[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.90[2]), (M.25.40.F.25.40.MCAR.cov.cl.90[2]), (M.25.40.F.40.50.MCAR.cov.cl.90[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.90[2]), (M.40.50.F.25.40.MCAR.cov.cl.90[2]), (M.40.50.F.40.50.MCAR.cov.cl.90[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.90.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.90.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")

# Cov 95

M.15.25.F.15.25.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.15.25.F.15.25)
M.25.40.F.15.25.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.25.40.F.15.25)
M.40.50.F.15.25.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.40.50.F.15.25)

M.15.25.F.25.40.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.15.25.F.25.40)
M.25.40.F.25.40.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.25.40.F.25.40)
M.40.50.F.25.40.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.40.50.F.25.40)

M.15.25.F.40.50.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.15.25.F.40.50)
M.25.40.F.40.50.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.25.40.F.40.50)
M.40.50.F.40.50.MCAR.cov.cl.95 <- quant.med(d.MCAR.cov.95$cov.MCAR.95.cl.M.40.50.F.40.50)



MCAR.cov.95.cl.age.groups.table <- matrix(c((M.15.25.F.15.25.MCAR.cov.cl.95[2]), (M.15.25.F.25.40.MCAR.cov.cl.95[2]), (M.15.25.F.40.50.MCAR.cov.cl.95[2]),
                                            (M.25.40.F.15.25.MCAR.cov.cl.95[2]), (M.25.40.F.25.40.MCAR.cov.cl.95[2]), (M.25.40.F.40.50.MCAR.cov.cl.95[2]),
                                            (M.40.50.F.15.25.MCAR.cov.cl.95[2]), (M.40.50.F.25.40.MCAR.cov.cl.95[2]), (M.40.50.F.40.50.MCAR.cov.cl.95[2])),
                                          ncol = 3,
                                          byrow = TRUE)

colnames(MCAR.cov.95.cl.age.groups.table) <- c("Female.15.25", "Female.25.40", "Female.40.50")
rownames(MCAR.cov.95.cl.age.groups.table) <- c("Male.15.25", "Male.25.40", "Male.40.50")



# Agregated table of pairings in transmission clusters  

agreggated.pairings.cl.mat <- matrix(c(M.15.25.F.15.25.MCAR.cov.cl.35[2], M.15.25.F.15.25.MCAR.cov.cl.40[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.45[2], M.15.25.F.15.25.MCAR.cov.cl.50[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.55[2], M.15.25.F.15.25.MCAR.cov.cl.60[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.65[2], M.15.25.F.15.25.MCAR.cov.cl.70[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.75[2], M.15.25.F.15.25.MCAR.cov.cl.80[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.85[2], M.15.25.F.15.25.MCAR.cov.cl.90[2], 
                                       M.15.25.F.15.25.MCAR.cov.cl.95[2], M.15.25.F.15.25.cov.100[2],
                                       
                                       M.25.40.F.15.25.MCAR.cov.cl.35[2], M.25.40.F.15.25.MCAR.cov.cl.40[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.45[2], M.25.40.F.15.25.MCAR.cov.cl.50[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.55[2], M.25.40.F.15.25.MCAR.cov.cl.60[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.65[2], M.25.40.F.15.25.MCAR.cov.cl.70[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.75[2], M.25.40.F.15.25.MCAR.cov.cl.80[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.85[2], M.25.40.F.15.25.MCAR.cov.cl.90[2], 
                                       M.25.40.F.15.25.MCAR.cov.cl.95[2], M.25.40.F.15.25.cov.100[2],
                                       
                                       M.40.50.F.15.25.MCAR.cov.cl.35[2], M.40.50.F.15.25.MCAR.cov.cl.40[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.45[2], M.40.50.F.15.25.MCAR.cov.cl.50[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.55[2], M.40.50.F.15.25.MCAR.cov.cl.60[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.65[2], M.40.50.F.15.25.MCAR.cov.cl.70[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.75[2], M.40.50.F.15.25.MCAR.cov.cl.80[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.85[2], M.40.50.F.15.25.MCAR.cov.cl.90[2], 
                                       M.40.50.F.15.25.MCAR.cov.cl.95[2], M.40.50.F.15.25.cov.100[2],
                                       
                                       M.15.25.F.25.40.MCAR.cov.cl.35[2], M.15.25.F.25.40.MCAR.cov.cl.40[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.45[2], M.15.25.F.25.40.MCAR.cov.cl.50[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.55[2], M.15.25.F.25.40.MCAR.cov.cl.60[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.65[2], M.15.25.F.25.40.MCAR.cov.cl.70[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.75[2], M.15.25.F.25.40.MCAR.cov.cl.80[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.85[2], M.15.25.F.25.40.MCAR.cov.cl.90[2], 
                                       M.15.25.F.25.40.MCAR.cov.cl.95[2], M.15.25.F.25.40.cov.100[2],
                                       
                                       M.25.40.F.25.40.MCAR.cov.cl.35[2], M.25.40.F.25.40.MCAR.cov.cl.40[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.45[2], M.25.40.F.25.40.MCAR.cov.cl.50[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.55[2], M.25.40.F.25.40.MCAR.cov.cl.60[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.65[2], M.25.40.F.25.40.MCAR.cov.cl.70[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.75[2], M.25.40.F.25.40.MCAR.cov.cl.80[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.85[2], M.25.40.F.25.40.MCAR.cov.cl.90[2], 
                                       M.25.40.F.25.40.MCAR.cov.cl.95[2], M.25.40.F.25.40.cov.100[2],
                                       
                                       M.40.50.F.25.40.MCAR.cov.cl.35[2], M.40.50.F.25.40.MCAR.cov.cl.40[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.45[2], M.40.50.F.25.40.MCAR.cov.cl.50[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.55[2], M.40.50.F.25.40.MCAR.cov.cl.60[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.65[2], M.40.50.F.25.40.MCAR.cov.cl.70[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.75[2], M.40.50.F.25.40.MCAR.cov.cl.80[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.85[2], M.40.50.F.25.40.MCAR.cov.cl.90[2], 
                                       M.40.50.F.25.40.MCAR.cov.cl.95[2], M.40.50.F.25.40.cov.100[2],
                                       
                                       M.15.25.F.40.50.MCAR.cov.cl.35[2], M.15.25.F.40.50.MCAR.cov.cl.40[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.45[2], M.15.25.F.40.50.MCAR.cov.cl.50[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.55[2], M.15.25.F.40.50.MCAR.cov.cl.60[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.65[2], M.15.25.F.40.50.MCAR.cov.cl.70[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.75[2], M.15.25.F.40.50.MCAR.cov.cl.80[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.85[2], M.15.25.F.40.50.MCAR.cov.cl.90[2], 
                                       M.15.25.F.40.50.MCAR.cov.cl.95[2], M.15.25.F.40.50.cov.100[2],
                                       
                                       M.25.40.F.40.50.MCAR.cov.cl.35[2], M.25.40.F.40.50.MCAR.cov.cl.40[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.45[2], M.25.40.F.40.50.MCAR.cov.cl.50[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.55[2], M.25.40.F.40.50.MCAR.cov.cl.60[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.65[2], M.25.40.F.40.50.MCAR.cov.cl.70[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.75[2], M.25.40.F.40.50.MCAR.cov.cl.80[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.85[2], M.25.40.F.40.50.MCAR.cov.cl.90[2], 
                                       M.25.40.F.40.50.MCAR.cov.cl.95[2], M.25.40.F.40.50.cov.100[2],
                                       
                                       M.40.50.F.40.50.MCAR.cov.cl.35[2], M.40.50.F.40.50.MCAR.cov.cl.40[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.45[2], M.40.50.F.40.50.MCAR.cov.cl.50[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.55[2], M.40.50.F.40.50.MCAR.cov.cl.60[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.65[2], M.40.50.F.40.50.MCAR.cov.cl.70[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.75[2], M.40.50.F.40.50.MCAR.cov.cl.80[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.85[2], M.40.50.F.40.50.MCAR.cov.cl.90[2], 
                                       M.40.50.F.40.50.MCAR.cov.cl.95[2], M.40.50.F.40.50.cov.100[2]),
                                     
                                     ncol = 14,
                                     byrow = TRUE)



colnames(agreggated.pairings.cl.mat) <- c("cl.cov.35", "cl.cov.40", "cl.cov.45",
                                          "cl.cov.50", "cl.cov.55", "cl.cov.60",
                                          "cl.cov.65", "cl.cov.70", "cl.cov.75",
                                          "cl.cov.80", "cl.cov.85", "cl.cov.90",
                                          "cl.cov.95", "true.cov.100")

rownames(agreggated.pairings.cl.mat) <- c("M.15.25.F.15.25", "M.25.40.F.15.25", "M.40.50.F.15.25",
                                          "M.15.25.F.25.40", "M.25.40.F.25.40", "M.40.50.F.25.40",
                                          "M.15.25.F.40.50", "M.25.40.F.40.50", "M.40.50.F.40.50")

agreggated.pairings.cl.mat

```


# Proportions of pairings across age groups


## True proportions at 100% coverage

True proprotions of men/women in pairing at 100 coverage.

```{r prop_pairings}

dr.cov.100 <- dr %>%
  select(contains(".100"))

d.MCAR.cov.100.prop.men <-  dr.cov.100 %>%
  select(contains("true.prop.men")) # true proportion of pairings inferred 

d.MCAR.cov.100.prop.women <-  dr.cov.100 %>%
  select(contains("true.prop.women")) 



vector.MCAR.true.cov.100.prop.men15.25.F.15.25 <- d.MCAR.cov.100.prop.men[,1]
vector.MCAR.true.cov.100.prop.women15.25.M.15.25 <- d.MCAR.cov.100.prop.women[,1]

vector.MCAR.true.cov.100.prop.men25.40.F.15.25 <- d.MCAR.cov.100.prop.men[,2]
vector.MCAR.true.cov.100.prop.women25.40.M.15.25 <- d.MCAR.cov.100.prop.women[,2]

vector.MCAR.true.cov.100.prop.men40.50.F.15.25 <- d.MCAR.cov.100.prop.men[,3]
vector.MCAR.true.cov.100.prop.women40.50.M.15.25 <- d.MCAR.cov.100.prop.women[,3]

vector.MCAR.true.cov.100.prop.men15.25.F.25.40 <- d.MCAR.cov.100.prop.men[,4]
vector.MCAR.true.cov.100.prop.women15.25.M.25.40 <- d.MCAR.cov.100.prop.women[,4]

vector.MCAR.true.cov.100.prop.men25.40.F.25.40 <- d.MCAR.cov.100.prop.men[,5]
vector.MCAR.true.cov.100.prop.women25.40.M.25.40 <- d.MCAR.cov.100.prop.women[,5]

vector.MCAR.true.cov.100.prop.men40.50.F.25.40 <- d.MCAR.cov.100.prop.men[,6]
vector.MCAR.true.cov.100.prop.women40.50.M.25.40 <- d.MCAR.cov.100.prop.women[,6]


vector.MCAR.true.cov.100.prop.men15.25.F.40.50 <- d.MCAR.cov.100.prop.men[,7]
vector.MCAR.true.cov.100.prop.women15.25.M.40.50 <- d.MCAR.cov.100.prop.women[,7]

vector.MCAR.true.cov.100.prop.men25.40.F.40.50 <- d.MCAR.cov.100.prop.men[,8]
vector.MCAR.true.cov.100.prop.women25.40.M.40.50 <- d.MCAR.cov.100.prop.women[,8]

vector.MCAR.true.cov.100.prop.men40.50.F.40.50 <- d.MCAR.cov.100.prop.men[,9]
vector.MCAR.true.cov.100.prop.women40.50.M.40.50 <- d.MCAR.cov.100.prop.women[,9]


# Summarrised

d.MCAR.true.cov.100.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.100.prop.men[,1])
d.MCAR.true.cov.100.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.100.prop.women[,1])

d.MCAR.true.cov.100.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.100.prop.men[,2])
d.MCAR.true.cov.100.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.100.prop.women[,2])

d.MCAR.true.cov.100.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.100.prop.men[,3])
d.MCAR.true.cov.100.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.100.prop.women[,3])

d.MCAR.true.cov.100.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.100.prop.men[,4])
d.MCAR.true.cov.100.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.100.prop.women[,4])

d.MCAR.true.cov.100.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.100.prop.men[,5])
d.MCAR.true.cov.100.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.100.prop.women[,5])

d.MCAR.true.cov.100.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.100.prop.men[,6])
d.MCAR.true.cov.100.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.100.prop.women[,6])


d.MCAR.true.cov.100.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.100.prop.men[,7])
d.MCAR.true.cov.100.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.100.prop.women[,7])

d.MCAR.true.cov.100.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.100.prop.men[,8])
d.MCAR.true.cov.100.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.100.prop.women[,8])

d.MCAR.true.cov.100.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.100.prop.men[,9])
d.MCAR.true.cov.100.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.100.prop.women[,9])

props.val.F <- c(d.MCAR.true.cov.100.prop.men15.25.F.15.25[2], d.MCAR.true.cov.100.prop.women15.25.M.15.25[2],
                 d.MCAR.true.cov.100.prop.men25.40.F.15.25[2], d.MCAR.true.cov.100.prop.women25.40.M.15.25[2],
                 d.MCAR.true.cov.100.prop.men40.50.F.15.25[2], d.MCAR.true.cov.100.prop.women40.50.M.15.25[2],
                 d.MCAR.true.cov.100.prop.men15.25.F.25.40[2], d.MCAR.true.cov.100.prop.women15.25.M.25.40[2],
                 d.MCAR.true.cov.100.prop.men25.40.F.25.40[2], d.MCAR.true.cov.100.prop.women25.40.M.25.40[2],
                 d.MCAR.true.cov.100.prop.men40.50.F.25.40[2], d.MCAR.true.cov.100.prop.women40.50.M.25.40[2],
                 d.MCAR.true.cov.100.prop.men15.25.F.40.50[2], d.MCAR.true.cov.100.prop.women15.25.M.40.50[2],
                 d.MCAR.true.cov.100.prop.men25.40.F.40.50[2], d.MCAR.true.cov.100.prop.women25.40.M.40.50[2],
                 d.MCAR.true.cov.100.prop.men40.50.F.40.50[2], d.MCAR.true.cov.100.prop.women40.50.M.40.50[2])

props.val.U <- c(d.MCAR.true.cov.100.prop.men15.25.F.15.25[3], d.MCAR.true.cov.100.prop.women15.25.M.15.25[3],
                 d.MCAR.true.cov.100.prop.men25.40.F.15.25[3], d.MCAR.true.cov.100.prop.women25.40.M.15.25[3],
                 d.MCAR.true.cov.100.prop.men40.50.F.15.25[3], d.MCAR.true.cov.100.prop.women40.50.M.15.25[3],
                 d.MCAR.true.cov.100.prop.men15.25.F.25.40[3], d.MCAR.true.cov.100.prop.women15.25.M.25.40[3],
                 d.MCAR.true.cov.100.prop.men25.40.F.25.40[3], d.MCAR.true.cov.100.prop.women25.40.M.25.40[3],
                 d.MCAR.true.cov.100.prop.men40.50.F.25.40[3], d.MCAR.true.cov.100.prop.women40.50.M.25.40[3],
                 d.MCAR.true.cov.100.prop.men15.25.F.40.50[3], d.MCAR.true.cov.100.prop.women15.25.M.40.50[3],
                 d.MCAR.true.cov.100.prop.men25.40.F.40.50[3], d.MCAR.true.cov.100.prop.women25.40.M.40.50[3],
                 d.MCAR.true.cov.100.prop.men40.50.F.40.50[3], d.MCAR.true.cov.100.prop.women40.50.M.40.50[3])



props.val.L <- c(d.MCAR.true.cov.100.prop.men15.25.F.15.25[1], d.MCAR.true.cov.100.prop.women15.25.M.15.25[1],
                 d.MCAR.true.cov.100.prop.men25.40.F.15.25[1], d.MCAR.true.cov.100.prop.women25.40.M.15.25[1],
                 d.MCAR.true.cov.100.prop.men40.50.F.15.25[1], d.MCAR.true.cov.100.prop.women40.50.M.15.25[1],
                 d.MCAR.true.cov.100.prop.men15.25.F.25.40[1], d.MCAR.true.cov.100.prop.women15.25.M.25.40[1],
                 d.MCAR.true.cov.100.prop.men25.40.F.25.40[1], d.MCAR.true.cov.100.prop.women25.40.M.25.40[1],
                 d.MCAR.true.cov.100.prop.men40.50.F.25.40[1], d.MCAR.true.cov.100.prop.women40.50.M.25.40[1],
                 d.MCAR.true.cov.100.prop.men15.25.F.40.50[1], d.MCAR.true.cov.100.prop.women15.25.M.40.50[1],
                 d.MCAR.true.cov.100.prop.men25.40.F.40.50[1], d.MCAR.true.cov.100.prop.women25.40.M.40.50[1],
                 d.MCAR.true.cov.100.prop.men40.50.F.40.50[1], d.MCAR.true.cov.100.prop.women40.50.M.40.50[1])

names.props <- c("M.15.25.F.15.25", "W.15.25.M.15.25", "M.25.40.F.15.25", "W.25.40.M.15.25",
                 "M.40.50.F.15.25", "W.40.50.M.15.25", "M.15.25.F.25.40", "W.15.25.M.25.40",
                 "M.25.40.F.25.40", "W.25.40.M.25.40", "M.40.50.F.25.40", "W.40.50.M.25.40",
                 "M.15.25.F.40.50", "W.15.25.M.40.50", "M.25.40.F.40.50", "W.25.40.M.40.50",
                 "M.40.50.F.40.50", "W.40.50.M.40.50")


props.table <- data.frame(names.props, props.val.F, props.val.L, props.val.U)



```


## Proportions in different sequence coverage scenarios

Proportions of men/women inferred from pairings in transmission clusters.


```{r proprt_seq_cov}

# Extracting data

# Proportions of pairing of men/women across different age groups in three cases

# (i) transmission network built from transmission clusters
# .cl.prop.men
# .cl.prop.women

# (ii) true proportions in true transmission network of these individuals in transmission clusters
# .cl.true.prop.men
# .cl.true.prop.women


# cov 35

d.MCAR.cov.35.cl.prop.men <-  d.MCAR.cov.35 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.35.cl.prop.women <-  d.MCAR.cov.35 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.35.cl.true.prop.men <-  d.MCAR.cov.35 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.35.cl.true.prop.women <-  d.MCAR.cov.35 %>%
  select(contains(".cl.true.prop.women")) 



# cov 40

d.MCAR.cov.40.cl.prop.men <-  d.MCAR.cov.40 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.40.cl.prop.women <-  d.MCAR.cov.40 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.40.cl.true.prop.men <-  d.MCAR.cov.40 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.40.cl.true.prop.women <-  d.MCAR.cov.40 %>%
  select(contains(".cl.true.prop.women")) 


# cov 45

d.MCAR.cov.45.cl.prop.men <-  d.MCAR.cov.45 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.45.cl.prop.women <-  d.MCAR.cov.45 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.45.cl.true.prop.men <-  d.MCAR.cov.45 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.45.cl.true.prop.women <-  d.MCAR.cov.45 %>%
  select(contains(".cl.true.prop.women")) 



# cov 50

d.MCAR.cov.50.cl.prop.men <-  d.MCAR.cov.50 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.50.cl.prop.women <-  d.MCAR.cov.50 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.50.cl.true.prop.men <-  d.MCAR.cov.50 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.50.cl.true.prop.women <-  d.MCAR.cov.50 %>%
  select(contains(".cl.true.prop.women")) 



# cov 55

d.MCAR.cov.55.cl.prop.men <-  d.MCAR.cov.55 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.55.cl.prop.women <-  d.MCAR.cov.55 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.55.cl.true.prop.men <-  d.MCAR.cov.55 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.55.cl.true.prop.women <-  d.MCAR.cov.55 %>%
  select(contains(".cl.true.prop.women")) 



# cov 60

d.MCAR.cov.60.cl.prop.men <-  d.MCAR.cov.60 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.60.cl.prop.women <-  d.MCAR.cov.60 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.60.cl.true.prop.men <-  d.MCAR.cov.60 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.60.cl.true.prop.women <-  d.MCAR.cov.60 %>%
  select(contains(".cl.true.prop.women")) 



# 65

d.MCAR.cov.65.cl.prop.men <-  d.MCAR.cov.65 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.65.cl.prop.women <-  d.MCAR.cov.65 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.65.cl.true.prop.men <-  d.MCAR.cov.65 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.65.cl.true.prop.women <-  d.MCAR.cov.65 %>%
  select(contains(".cl.true.prop.women")) 



# 70

d.MCAR.cov.70.cl.prop.men <-  d.MCAR.cov.70 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.70.cl.prop.women <-  d.MCAR.cov.70 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.70.cl.true.prop.men <-  d.MCAR.cov.70 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.70.cl.true.prop.women <-  d.MCAR.cov.70 %>%
  select(contains(".cl.true.prop.women")) 



# 75

d.MCAR.cov.75.cl.prop.men <-  d.MCAR.cov.75 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.75.cl.prop.women <-  d.MCAR.cov.75 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.75.cl.true.prop.men <-  d.MCAR.cov.75 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.75.cl.true.prop.women <-  d.MCAR.cov.75 %>%
  select(contains(".cl.true.prop.women")) 



# cov 80

d.MCAR.cov.80.cl.prop.men <-  d.MCAR.cov.80 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.80.cl.prop.women <-  d.MCAR.cov.80 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.80.cl.true.prop.men <-  d.MCAR.cov.80 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.80.cl.true.prop.women <-  d.MCAR.cov.80 %>%
  select(contains(".cl.true.prop.women")) 



# cov 85

d.MCAR.cov.85.cl.prop.men <-  d.MCAR.cov.85 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.85.cl.prop.women <-  d.MCAR.cov.85 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.85.cl.true.prop.men <-  d.MCAR.cov.85 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.85.cl.true.prop.women <-  d.MCAR.cov.85 %>%
  select(contains(".cl.true.prop.women")) 



# cov 90

d.MCAR.cov.90.cl.prop.men <-  d.MCAR.cov.90 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.90.cl.prop.women <-  d.MCAR.cov.90 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.90.cl.true.prop.men <-  d.MCAR.cov.90 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.90.cl.true.prop.women <-  d.MCAR.cov.90 %>%
  select(contains(".cl.true.prop.women")) 



# cov 95


d.MCAR.cov.95.cl.prop.men <-  d.MCAR.cov.95 %>%
  select(contains(".cl.prop.men")) # proportion of pairings inferred from transmission clusters

d.MCAR.cov.95.cl.prop.women <-  d.MCAR.cov.95 %>%
  select(contains(".cl.prop.women")) 

d.MCAR.cov.95.cl.true.prop.men <-  d.MCAR.cov.95 %>%
  select(contains(".cl.true.prop.men"))  # true proportion of pairings in transmission clusters

d.MCAR.cov.95.cl.true.prop.women <-  d.MCAR.cov.95 %>%
  select(contains(".cl.true.prop.women")) 




# proportions computation


# Cov 35


# Vectors

vector.MCAR.cov.35.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.35.cl.prop.men[,1]
vector.MCAR.cov.35.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.35.cl.prop.women[,1]

vector.MCAR.cov.35.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.35.cl.prop.men[,2]
vector.MCAR.cov.35.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.35.cl.prop.women[,2]

vector.MCAR.cov.35.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.35.cl.prop.men[,3]
vector.MCAR.cov.35.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.35.cl.prop.women[,3]

vector.MCAR.cov.35.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.35.cl.prop.men[,4]
vector.MCAR.cov.35.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.35.cl.prop.women[,4]

vector.MCAR.cov.35.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.35.cl.prop.men[,5]
vector.MCAR.cov.35.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.35.cl.prop.women[,5]

vector.MCAR.cov.35.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.35.cl.prop.men[,6]
vector.MCAR.cov.35.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.35.cl.prop.women[,6]


vector.MCAR.cov.35.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.35.cl.prop.men[,7]
vector.MCAR.cov.35.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.35.cl.prop.women[,7]

vector.MCAR.cov.35.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.35.cl.prop.men[,8]
vector.MCAR.cov.35.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.35.cl.prop.women[,8]

vector.MCAR.cov.35.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.35.cl.prop.men[,9]
vector.MCAR.cov.35.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.35.cl.prop.women[,9]



# Summarised

d.MCAR.cov.35.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.men[,1])
d.MCAR.cov.35.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.women[,1])

d.MCAR.cov.35.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.men[,2])
d.MCAR.cov.35.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.women[,2])

d.MCAR.cov.35.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.men[,3])
d.MCAR.cov.35.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.35.cl.prop.women[,3])

d.MCAR.cov.35.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.men[,4])
d.MCAR.cov.35.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.women[,4])

d.MCAR.cov.35.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.men[,5])
d.MCAR.cov.35.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.women[,5])

d.MCAR.cov.35.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.men[,6])
d.MCAR.cov.35.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.35.cl.prop.women[,6])


d.MCAR.cov.35.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.men[,7])
d.MCAR.cov.35.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.women[,7])

d.MCAR.cov.35.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.men[,8])
d.MCAR.cov.35.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.women[,8])

d.MCAR.cov.35.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.men[,9])
d.MCAR.cov.35.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.35.cl.prop.women[,9])


# Cov 40


# Vector


vector.MCAR.cov.40.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.40.cl.prop.men[,1]
vector.MCAR.cov.40.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.40.cl.prop.women[,1]

vector.MCAR.cov.40.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.40.cl.prop.men[,2]
vector.MCAR.cov.40.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.40.cl.prop.women[,2]

vector.MCAR.cov.40.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.40.cl.prop.men[,3]
vector.MCAR.cov.40.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.40.cl.prop.women[,3]

vector.MCAR.cov.40.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.40.cl.prop.men[,4]
vector.MCAR.cov.40.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.40.cl.prop.women[,4]

vector.MCAR.cov.40.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.40.cl.prop.men[,5]
vector.MCAR.cov.40.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.40.cl.prop.women[,5]

vector.MCAR.cov.40.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.40.cl.prop.men[,6]
vector.MCAR.cov.40.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.40.cl.prop.women[,6]


vector.MCAR.cov.40.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.40.cl.prop.men[,7]
vector.MCAR.cov.40.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.40.cl.prop.women[,7]

vector.MCAR.cov.40.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.40.cl.prop.men[,8]
vector.MCAR.cov.40.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.40.cl.prop.women[,8]

vector.MCAR.cov.40.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.40.cl.prop.men[,9]
vector.MCAR.cov.40.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.40.cl.prop.women[,9]



# Summarised

d.MCAR.cov.40.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.men[,1])
d.MCAR.cov.40.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.women[,1])

d.MCAR.cov.40.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.men[,2])
d.MCAR.cov.40.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.women[,2])

d.MCAR.cov.40.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.men[,3])
d.MCAR.cov.40.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.40.cl.prop.women[,3])

d.MCAR.cov.40.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.men[,4])
d.MCAR.cov.40.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.women[,4])

d.MCAR.cov.40.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.men[,5])
d.MCAR.cov.40.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.women[,5])

d.MCAR.cov.40.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.men[,6])
d.MCAR.cov.40.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.40.cl.prop.women[,6])


d.MCAR.cov.40.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.men[,7])
d.MCAR.cov.40.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.women[,7])

d.MCAR.cov.40.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.men[,8])
d.MCAR.cov.40.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.women[,8])

d.MCAR.cov.40.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.men[,9])
d.MCAR.cov.40.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.40.cl.prop.women[,9])


# Cov 45


# Vector


vector.MCAR.cov.45.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.45.cl.prop.men[,1]
vector.MCAR.cov.45.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.45.cl.prop.women[,1]

vector.MCAR.cov.45.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.45.cl.prop.men[,2]
vector.MCAR.cov.45.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.45.cl.prop.women[,2]

vector.MCAR.cov.45.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.45.cl.prop.men[,3]
vector.MCAR.cov.45.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.45.cl.prop.women[,3]

vector.MCAR.cov.45.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.45.cl.prop.men[,4]
vector.MCAR.cov.45.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.45.cl.prop.women[,4]

vector.MCAR.cov.45.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.45.cl.prop.men[,5]
vector.MCAR.cov.45.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.45.cl.prop.women[,5]

vector.MCAR.cov.45.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.45.cl.prop.men[,6]
vector.MCAR.cov.45.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.45.cl.prop.women[,6]


vector.MCAR.cov.45.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.45.cl.prop.men[,7]
vector.MCAR.cov.45.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.45.cl.prop.women[,7]

vector.MCAR.cov.45.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.45.cl.prop.men[,8]
vector.MCAR.cov.45.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.45.cl.prop.women[,8]

vector.MCAR.cov.45.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.45.cl.prop.men[,9]
vector.MCAR.cov.45.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.45.cl.prop.women[,9]



# Summarised

d.MCAR.cov.45.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.men[,1])
d.MCAR.cov.45.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.women[,1])

d.MCAR.cov.45.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.men[,2])
d.MCAR.cov.45.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.women[,2])

d.MCAR.cov.45.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.men[,3])
d.MCAR.cov.45.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.45.cl.prop.women[,3])

d.MCAR.cov.45.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.men[,4])
d.MCAR.cov.45.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.women[,4])

d.MCAR.cov.45.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.men[,5])
d.MCAR.cov.45.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.women[,5])

d.MCAR.cov.45.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.men[,6])
d.MCAR.cov.45.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.45.cl.prop.women[,6])


d.MCAR.cov.45.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.men[,7])
d.MCAR.cov.45.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.women[,7])

d.MCAR.cov.45.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.men[,8])
d.MCAR.cov.45.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.women[,8])

d.MCAR.cov.45.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.men[,9])
d.MCAR.cov.45.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.45.cl.prop.women[,9])




# Cov 50


# Vector


vector.MCAR.cov.50.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.50.cl.prop.men[,1]
vector.MCAR.cov.50.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.50.cl.prop.women[,1]

vector.MCAR.cov.50.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.50.cl.prop.men[,2]
vector.MCAR.cov.50.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.50.cl.prop.women[,2]

vector.MCAR.cov.50.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.50.cl.prop.men[,3]
vector.MCAR.cov.50.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.50.cl.prop.women[,3]

vector.MCAR.cov.50.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.50.cl.prop.men[,4]
vector.MCAR.cov.50.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.50.cl.prop.women[,4]

vector.MCAR.cov.50.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.50.cl.prop.men[,5]
vector.MCAR.cov.50.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.50.cl.prop.women[,5]

vector.MCAR.cov.50.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.50.cl.prop.men[,6]
vector.MCAR.cov.50.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.50.cl.prop.women[,6]


vector.MCAR.cov.50.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.50.cl.prop.men[,7]
vector.MCAR.cov.50.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.50.cl.prop.women[,7]

vector.MCAR.cov.50.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.50.cl.prop.men[,8]
vector.MCAR.cov.50.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.50.cl.prop.women[,8]

vector.MCAR.cov.50.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.50.cl.prop.men[,9]
vector.MCAR.cov.50.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.50.cl.prop.women[,9]


# Summarised

d.MCAR.cov.50.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.men[,1])
d.MCAR.cov.50.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.women[,1])

d.MCAR.cov.50.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.men[,2])
d.MCAR.cov.50.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.women[,2])

d.MCAR.cov.50.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.men[,3])
d.MCAR.cov.50.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.50.cl.prop.women[,3])

d.MCAR.cov.50.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.men[,4])
d.MCAR.cov.50.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.women[,4])

d.MCAR.cov.50.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.men[,5])
d.MCAR.cov.50.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.women[,5])

d.MCAR.cov.50.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.men[,6])
d.MCAR.cov.50.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.50.cl.prop.women[,6])


d.MCAR.cov.50.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.men[,7])
d.MCAR.cov.50.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.women[,7])

d.MCAR.cov.50.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.men[,8])
d.MCAR.cov.50.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.women[,8])

d.MCAR.cov.50.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.men[,9])
d.MCAR.cov.50.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.50.cl.prop.women[,9])



# Cov 55


# Vector


vector.MCAR.cov.55.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.55.cl.prop.men[,1]
vector.MCAR.cov.55.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.55.cl.prop.women[,1]

vector.MCAR.cov.55.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.55.cl.prop.men[,2]
vector.MCAR.cov.55.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.55.cl.prop.women[,2]

vector.MCAR.cov.55.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.55.cl.prop.men[,3]
vector.MCAR.cov.55.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.55.cl.prop.women[,3]

vector.MCAR.cov.55.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.55.cl.prop.men[,4]
vector.MCAR.cov.55.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.55.cl.prop.women[,4]

vector.MCAR.cov.55.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.55.cl.prop.men[,5]
vector.MCAR.cov.55.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.55.cl.prop.women[,5]

vector.MCAR.cov.55.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.55.cl.prop.men[,6]
vector.MCAR.cov.55.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.55.cl.prop.women[,6]


vector.MCAR.cov.55.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.55.cl.prop.men[,7]
vector.MCAR.cov.55.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.55.cl.prop.women[,7]

vector.MCAR.cov.55.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.55.cl.prop.men[,8]
vector.MCAR.cov.55.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.55.cl.prop.women[,8]

vector.MCAR.cov.55.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.55.cl.prop.men[,9]
vector.MCAR.cov.55.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.55.cl.prop.women[,9]


# Summarised

d.MCAR.cov.55.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.men[,1])
d.MCAR.cov.55.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.women[,1])

d.MCAR.cov.55.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.men[,2])
d.MCAR.cov.55.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.women[,2])

d.MCAR.cov.55.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.men[,3])
d.MCAR.cov.55.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.55.cl.prop.women[,3])

d.MCAR.cov.55.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.men[,4])
d.MCAR.cov.55.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.women[,4])

d.MCAR.cov.55.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.men[,5])
d.MCAR.cov.55.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.women[,5])

d.MCAR.cov.55.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.men[,6])
d.MCAR.cov.55.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.55.cl.prop.women[,6])


d.MCAR.cov.55.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.men[,7])
d.MCAR.cov.55.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.women[,7])

d.MCAR.cov.55.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.men[,8])
d.MCAR.cov.55.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.women[,8])

d.MCAR.cov.55.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.men[,9])
d.MCAR.cov.55.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.55.cl.prop.women[,9])



# Cov 60


# Vector


vector.MCAR.cov.60.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.60.cl.prop.men[,1]
vector.MCAR.cov.60.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.60.cl.prop.women[,1]

vector.MCAR.cov.60.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.60.cl.prop.men[,2]
vector.MCAR.cov.60.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.60.cl.prop.women[,2]

vector.MCAR.cov.60.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.60.cl.prop.men[,3]
vector.MCAR.cov.60.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.60.cl.prop.women[,3]

vector.MCAR.cov.60.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.60.cl.prop.men[,4]
vector.MCAR.cov.60.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.60.cl.prop.women[,4]

vector.MCAR.cov.60.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.60.cl.prop.men[,5]
vector.MCAR.cov.60.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.60.cl.prop.women[,5]

vector.MCAR.cov.60.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.60.cl.prop.men[,6]
vector.MCAR.cov.60.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.60.cl.prop.women[,6]


vector.MCAR.cov.60.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.60.cl.prop.men[,7]
vector.MCAR.cov.60.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.60.cl.prop.women[,7]

vector.MCAR.cov.60.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.60.cl.prop.men[,8]
vector.MCAR.cov.60.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.60.cl.prop.women[,8]

vector.MCAR.cov.60.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.60.cl.prop.men[,9]
vector.MCAR.cov.60.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.60.cl.prop.women[,9]


# Summarised

d.MCAR.cov.60.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.men[,1])
d.MCAR.cov.60.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.women[,1])

d.MCAR.cov.60.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.men[,2])
d.MCAR.cov.60.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.women[,2])

d.MCAR.cov.60.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.men[,3])
d.MCAR.cov.60.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.60.cl.prop.women[,3])

d.MCAR.cov.60.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.men[,4])
d.MCAR.cov.60.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.women[,4])

d.MCAR.cov.60.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.men[,5])
d.MCAR.cov.60.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.women[,5])

d.MCAR.cov.60.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.men[,6])
d.MCAR.cov.60.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.60.cl.prop.women[,6])


d.MCAR.cov.60.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.men[,7])
d.MCAR.cov.60.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.women[,7])

d.MCAR.cov.60.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.men[,8])
d.MCAR.cov.60.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.women[,8])

d.MCAR.cov.60.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.men[,9])
d.MCAR.cov.60.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.60.cl.prop.women[,9])



# Cov 65


# Vector


vector.MCAR.cov.65.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.65.cl.prop.men[,1]
vector.MCAR.cov.65.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.65.cl.prop.women[,1]

vector.MCAR.cov.65.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.65.cl.prop.men[,2]
vector.MCAR.cov.65.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.65.cl.prop.women[,2]

vector.MCAR.cov.65.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.65.cl.prop.men[,3]
vector.MCAR.cov.65.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.65.cl.prop.women[,3]

vector.MCAR.cov.65.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.65.cl.prop.men[,4]
vector.MCAR.cov.65.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.65.cl.prop.women[,4]

vector.MCAR.cov.65.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.65.cl.prop.men[,5]
vector.MCAR.cov.65.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.65.cl.prop.women[,5]

vector.MCAR.cov.65.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.65.cl.prop.men[,6]
vector.MCAR.cov.65.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.65.cl.prop.women[,6]


vector.MCAR.cov.65.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.65.cl.prop.men[,7]
vector.MCAR.cov.65.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.65.cl.prop.women[,7]

vector.MCAR.cov.65.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.65.cl.prop.men[,8]
vector.MCAR.cov.65.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.65.cl.prop.women[,8]

vector.MCAR.cov.65.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.65.cl.prop.men[,9]
vector.MCAR.cov.65.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.65.cl.prop.women[,9]



# Summarised

d.MCAR.cov.65.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.men[,1])
d.MCAR.cov.65.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.women[,1])

d.MCAR.cov.65.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.men[,2])
d.MCAR.cov.65.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.women[,2])

d.MCAR.cov.65.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.men[,3])
d.MCAR.cov.65.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.65.cl.prop.women[,3])

d.MCAR.cov.65.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.men[,4])
d.MCAR.cov.65.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.women[,4])

d.MCAR.cov.65.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.men[,5])
d.MCAR.cov.65.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.women[,5])

d.MCAR.cov.65.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.men[,6])
d.MCAR.cov.65.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.65.cl.prop.women[,6])


d.MCAR.cov.65.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.men[,7])
d.MCAR.cov.65.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.women[,7])

d.MCAR.cov.65.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.men[,8])
d.MCAR.cov.65.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.women[,8])

d.MCAR.cov.65.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.men[,9])
d.MCAR.cov.65.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.65.cl.prop.women[,9])


# Cov 70


# Vector


vector.MCAR.cov.70.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.70.cl.prop.men[,1]
vector.MCAR.cov.70.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.70.cl.prop.women[,1]

vector.MCAR.cov.70.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.70.cl.prop.men[,2]
vector.MCAR.cov.70.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.70.cl.prop.women[,2]

vector.MCAR.cov.70.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.70.cl.prop.men[,3]
vector.MCAR.cov.70.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.70.cl.prop.women[,3]

vector.MCAR.cov.70.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.70.cl.prop.men[,4]
vector.MCAR.cov.70.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.70.cl.prop.women[,4]

vector.MCAR.cov.70.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.70.cl.prop.men[,5]
vector.MCAR.cov.70.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.70.cl.prop.women[,5]

vector.MCAR.cov.70.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.70.cl.prop.men[,6]
vector.MCAR.cov.70.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.70.cl.prop.women[,6]


vector.MCAR.cov.70.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.70.cl.prop.men[,7]
vector.MCAR.cov.70.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.70.cl.prop.women[,7]

vector.MCAR.cov.70.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.70.cl.prop.men[,8]
vector.MCAR.cov.70.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.70.cl.prop.women[,8]

vector.MCAR.cov.70.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.70.cl.prop.men[,9]
vector.MCAR.cov.70.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.70.cl.prop.women[,9]



# Summarised

d.MCAR.cov.70.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.men[,1])
d.MCAR.cov.70.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.women[,1])

d.MCAR.cov.70.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.men[,2])
d.MCAR.cov.70.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.women[,2])

d.MCAR.cov.70.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.men[,3])
d.MCAR.cov.70.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.70.cl.prop.women[,3])

d.MCAR.cov.70.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.men[,4])
d.MCAR.cov.70.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.women[,4])

d.MCAR.cov.70.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.men[,5])
d.MCAR.cov.70.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.women[,5])

d.MCAR.cov.70.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.men[,6])
d.MCAR.cov.70.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.70.cl.prop.women[,6])


d.MCAR.cov.70.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.men[,7])
d.MCAR.cov.70.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.women[,7])

d.MCAR.cov.70.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.men[,8])
d.MCAR.cov.70.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.women[,8])

d.MCAR.cov.70.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.men[,9])

d.MCAR.cov.70.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.70.cl.prop.women[,9])



# Cov 75


# Vector


vector.MCAR.cov.75.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.75.cl.prop.men[,1]
vector.MCAR.cov.75.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.75.cl.prop.women[,1]

vector.MCAR.cov.75.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.75.cl.prop.men[,2]
vector.MCAR.cov.75.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.75.cl.prop.women[,2]

vector.MCAR.cov.75.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.75.cl.prop.men[,3]
vector.MCAR.cov.75.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.75.cl.prop.women[,3]

vector.MCAR.cov.75.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.75.cl.prop.men[,4]
vector.MCAR.cov.75.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.75.cl.prop.women[,4]

vector.MCAR.cov.75.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.75.cl.prop.men[,5]
vector.MCAR.cov.75.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.75.cl.prop.women[,5]

vector.MCAR.cov.75.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.75.cl.prop.men[,6]
vector.MCAR.cov.75.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.75.cl.prop.women[,6]


vector.MCAR.cov.75.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.75.cl.prop.men[,7]
vector.MCAR.cov.75.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.75.cl.prop.women[,7]

vector.MCAR.cov.75.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.75.cl.prop.men[,8]
vector.MCAR.cov.75.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.75.cl.prop.women[,8]

vector.MCAR.cov.75.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.75.cl.prop.men[,9]
vector.MCAR.cov.75.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.75.cl.prop.women[,9]



# Summarised

d.MCAR.cov.75.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.men[,1])
d.MCAR.cov.75.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.women[,1])

d.MCAR.cov.75.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.men[,2])
d.MCAR.cov.75.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.women[,2])

d.MCAR.cov.75.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.men[,3])
d.MCAR.cov.75.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.75.cl.prop.women[,3])

d.MCAR.cov.75.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.men[,4])
d.MCAR.cov.75.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.women[,4])

d.MCAR.cov.75.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.men[,5])
d.MCAR.cov.75.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.women[,5])

d.MCAR.cov.75.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.men[,6])
d.MCAR.cov.75.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.75.cl.prop.women[,6])


d.MCAR.cov.75.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.men[,7])
d.MCAR.cov.75.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.women[,7])

d.MCAR.cov.75.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.men[,8])
d.MCAR.cov.75.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.women[,8])

d.MCAR.cov.75.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.men[,9])
d.MCAR.cov.75.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.75.cl.prop.women[,9])



# Cov 80


# Vector


vector.MCAR.cov.80.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.80.cl.prop.men[,1]
vector.MCAR.cov.80.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.80.cl.prop.women[,1]

vector.MCAR.cov.80.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.80.cl.prop.men[,2]
vector.MCAR.cov.80.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.80.cl.prop.women[,2]

vector.MCAR.cov.80.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.80.cl.prop.men[,3]
vector.MCAR.cov.80.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.80.cl.prop.women[,3]

vector.MCAR.cov.80.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.80.cl.prop.men[,4]
vector.MCAR.cov.80.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.80.cl.prop.women[,4]

vector.MCAR.cov.80.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.80.cl.prop.men[,5]
vector.MCAR.cov.80.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.80.cl.prop.women[,5]

vector.MCAR.cov.80.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.80.cl.prop.men[,6]
vector.MCAR.cov.80.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.80.cl.prop.women[,6]


vector.MCAR.cov.80.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.80.cl.prop.men[,7]
vector.MCAR.cov.80.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.80.cl.prop.women[,7]

vector.MCAR.cov.80.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.80.cl.prop.men[,8]
vector.MCAR.cov.80.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.80.cl.prop.women[,8]

vector.MCAR.cov.80.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.80.cl.prop.men[,9]
vector.MCAR.cov.80.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.80.cl.prop.women[,9]



# Summarised

d.MCAR.cov.80.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.men[,1])
d.MCAR.cov.80.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.women[,1])

d.MCAR.cov.80.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.men[,2])
d.MCAR.cov.80.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.women[,2])

d.MCAR.cov.80.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.men[,3])
d.MCAR.cov.80.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.80.cl.prop.women[,3])

d.MCAR.cov.80.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.men[,4])
d.MCAR.cov.80.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.women[,4])

d.MCAR.cov.80.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.men[,5])
d.MCAR.cov.80.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.women[,5])

d.MCAR.cov.80.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.men[,6])
d.MCAR.cov.80.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.80.cl.prop.women[,6])


d.MCAR.cov.80.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.men[,7])
d.MCAR.cov.80.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.women[,7])

d.MCAR.cov.80.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.men[,8])
d.MCAR.cov.80.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.women[,8])

d.MCAR.cov.80.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.men[,9])
d.MCAR.cov.80.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.80.cl.prop.women[,9])



# Cov 85


# Vector


vector.MCAR.cov.85.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.85.cl.prop.men[,1]
vector.MCAR.cov.85.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.85.cl.prop.women[,1]

vector.MCAR.cov.85.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.85.cl.prop.men[,2]
vector.MCAR.cov.85.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.85.cl.prop.women[,2]

vector.MCAR.cov.85.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.85.cl.prop.men[,3]
vector.MCAR.cov.85.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.85.cl.prop.women[,3]

vector.MCAR.cov.85.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.85.cl.prop.men[,4]
vector.MCAR.cov.85.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.85.cl.prop.women[,4]

vector.MCAR.cov.85.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.85.cl.prop.men[,5]
vector.MCAR.cov.85.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.85.cl.prop.women[,5]

vector.MCAR.cov.85.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.85.cl.prop.men[,6]
vector.MCAR.cov.85.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.85.cl.prop.women[,6]


vector.MCAR.cov.85.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.85.cl.prop.men[,7]
vector.MCAR.cov.85.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.85.cl.prop.women[,7]

vector.MCAR.cov.85.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.85.cl.prop.men[,8]
vector.MCAR.cov.85.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.85.cl.prop.women[,8]

vector.MCAR.cov.85.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.85.cl.prop.men[,9]
vector.MCAR.cov.85.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.85.cl.prop.women[,9]



# Summarised

d.MCAR.cov.85.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.men[,1])
d.MCAR.cov.85.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.women[,1])

d.MCAR.cov.85.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.men[,2])
d.MCAR.cov.85.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.women[,2])

d.MCAR.cov.85.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.men[,3])
d.MCAR.cov.85.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.85.cl.prop.women[,3])

d.MCAR.cov.85.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.men[,4])
d.MCAR.cov.85.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.women[,4])

d.MCAR.cov.85.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.men[,5])
d.MCAR.cov.85.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.women[,5])

d.MCAR.cov.85.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.men[,6])
d.MCAR.cov.85.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.85.cl.prop.women[,6])


d.MCAR.cov.85.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.men[,7])
d.MCAR.cov.85.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.women[,7])

d.MCAR.cov.85.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.men[,8])
d.MCAR.cov.85.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.women[,8])

d.MCAR.cov.85.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.men[,9])
d.MCAR.cov.85.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.85.cl.prop.women[,9])



# Cov 90


# Vector


vector.MCAR.cov.90.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.90.cl.prop.men[,1]
vector.MCAR.cov.90.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.90.cl.prop.women[,1]

vector.MCAR.cov.90.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.90.cl.prop.men[,2]
vector.MCAR.cov.90.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.90.cl.prop.women[,2]

vector.MCAR.cov.90.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.90.cl.prop.men[,3]
vector.MCAR.cov.90.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.90.cl.prop.women[,3]

vector.MCAR.cov.90.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.90.cl.prop.men[,4]
vector.MCAR.cov.90.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.90.cl.prop.women[,4]

vector.MCAR.cov.90.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.90.cl.prop.men[,5]
vector.MCAR.cov.90.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.90.cl.prop.women[,5]

vector.MCAR.cov.90.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.90.cl.prop.men[,6]
vector.MCAR.cov.90.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.90.cl.prop.women[,6]


vector.MCAR.cov.90.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.90.cl.prop.men[,7]
vector.MCAR.cov.90.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.90.cl.prop.women[,7]

vector.MCAR.cov.90.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.90.cl.prop.men[,8]
vector.MCAR.cov.90.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.90.cl.prop.women[,8]

vector.MCAR.cov.90.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.90.cl.prop.men[,9]
vector.MCAR.cov.90.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.90.cl.prop.women[,9]



# Summarised

d.MCAR.cov.90.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.men[,1])
d.MCAR.cov.90.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.women[,1])

d.MCAR.cov.90.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.men[,2])
d.MCAR.cov.90.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.women[,2])

d.MCAR.cov.90.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.men[,3])
d.MCAR.cov.90.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.90.cl.prop.women[,3])

d.MCAR.cov.90.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.men[,4])
d.MCAR.cov.90.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.women[,4])

d.MCAR.cov.90.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.men[,5])
d.MCAR.cov.90.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.women[,5])

d.MCAR.cov.90.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.men[,6])
d.MCAR.cov.90.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.90.cl.prop.women[,6])


d.MCAR.cov.90.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.men[,7])
d.MCAR.cov.90.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.women[,7])

d.MCAR.cov.90.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.men[,8])
d.MCAR.cov.90.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.women[,8])

d.MCAR.cov.90.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.men[,9])
d.MCAR.cov.90.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.90.cl.prop.women[,9])


# Cov 95


# Vector


vector.MCAR.cov.95.cl.prop.men15.25.F.15.25 <- d.MCAR.cov.95.cl.prop.men[,1]
vector.MCAR.cov.95.cl.prop.women15.25.M.15.25 <- d.MCAR.cov.95.cl.prop.women[,1]

vector.MCAR.cov.95.cl.prop.men25.40.F.15.25 <- d.MCAR.cov.95.cl.prop.men[,2]
vector.MCAR.cov.95.cl.prop.women25.40.M.15.25 <- d.MCAR.cov.95.cl.prop.women[,2]

vector.MCAR.cov.95.cl.prop.men40.50.F.15.25 <- d.MCAR.cov.95.cl.prop.men[,3]
vector.MCAR.cov.95.cl.prop.women40.50.M.15.25 <- d.MCAR.cov.95.cl.prop.women[,3]

vector.MCAR.cov.95.cl.prop.men15.25.F.25.40 <- d.MCAR.cov.95.cl.prop.men[,4]
vector.MCAR.cov.95.cl.prop.women15.25.M.25.40 <- d.MCAR.cov.95.cl.prop.women[,4]

vector.MCAR.cov.95.cl.prop.men25.40.F.25.40 <- d.MCAR.cov.95.cl.prop.men[,5]
vector.MCAR.cov.95.cl.prop.women25.40.M.25.40 <- d.MCAR.cov.95.cl.prop.women[,5]

vector.MCAR.cov.95.cl.prop.men40.50.F.25.40 <- d.MCAR.cov.95.cl.prop.men[,6]
vector.MCAR.cov.95.cl.prop.women40.50.M.25.40 <- d.MCAR.cov.95.cl.prop.women[,6]


vector.MCAR.cov.95.cl.prop.men15.25.F.40.50 <- d.MCAR.cov.95.cl.prop.men[,7]
vector.MCAR.cov.95.cl.prop.women15.25.M.40.50 <- d.MCAR.cov.95.cl.prop.women[,7]

vector.MCAR.cov.95.cl.prop.men25.40.F.40.50 <- d.MCAR.cov.95.cl.prop.men[,8]
vector.MCAR.cov.95.cl.prop.women25.40.M.40.50 <- d.MCAR.cov.95.cl.prop.women[,8]

vector.MCAR.cov.95.cl.prop.men40.50.F.40.50 <- d.MCAR.cov.95.cl.prop.men[,9]
vector.MCAR.cov.95.cl.prop.women40.50.M.40.50 <- d.MCAR.cov.95.cl.prop.women[,9]


# Summarised

d.MCAR.cov.95.cl.prop.men15.25.F.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.men[,1])
d.MCAR.cov.95.cl.prop.women15.25.M.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.women[,1])

d.MCAR.cov.95.cl.prop.men25.40.F.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.men[,2])

d.MCAR.cov.95.cl.prop.women25.40.M.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.women[,2])

d.MCAR.cov.95.cl.prop.men40.50.F.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.men[,3])
d.MCAR.cov.95.cl.prop.women40.50.M.15.25 <- quant.med(d.MCAR.cov.95.cl.prop.women[,3])

d.MCAR.cov.95.cl.prop.men15.25.F.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.men[,4])
d.MCAR.cov.95.cl.prop.women15.25.M.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.women[,4])

d.MCAR.cov.95.cl.prop.men25.40.F.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.men[,5])
d.MCAR.cov.95.cl.prop.women25.40.M.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.women[,5])

d.MCAR.cov.95.cl.prop.men40.50.F.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.men[,6])
d.MCAR.cov.95.cl.prop.women40.50.M.25.40 <- quant.med(d.MCAR.cov.95.cl.prop.women[,6])


d.MCAR.cov.95.cl.prop.men15.25.F.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.men[,7])
d.MCAR.cov.95.cl.prop.women15.25.M.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.women[,7])

d.MCAR.cov.95.cl.prop.men25.40.F.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.men[,8])
d.MCAR.cov.95.cl.prop.women25.40.M.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.women[,8])

d.MCAR.cov.95.cl.prop.men40.50.F.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.men[,9])
d.MCAR.cov.95.cl.prop.women40.50.M.40.50 <- quant.med(d.MCAR.cov.95.cl.prop.women[,9])



props_infer <- matrix(c(d.MCAR.cov.35.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.40.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.45.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.50.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.55.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.60.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.65.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.70.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.75.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.80.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.85.cl.prop.men15.25.F.15.25[2], d.MCAR.cov.90.cl.prop.men15.25.F.15.25[2], 
                  d.MCAR.cov.95.cl.prop.men15.25.F.15.25[2], d.MCAR.true.cov.100.prop.men15.25.F.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.40.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.45.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.50.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.55.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.60.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.65.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.70.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.75.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.80.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.85.cl.prop.women15.25.M.15.25[2], d.MCAR.cov.90.cl.prop.women15.25.M.15.25[2], 
                  d.MCAR.cov.95.cl.prop.women15.25.M.15.25[2], d.MCAR.true.cov.100.prop.women15.25.M.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.40.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.45.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.50.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.55.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.60.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.65.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.70.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.75.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.80.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.85.cl.prop.men25.40.F.15.25[2], d.MCAR.cov.90.cl.prop.men25.40.F.15.25[2], 
                  d.MCAR.cov.95.cl.prop.men25.40.F.15.25[2], d.MCAR.true.cov.100.prop.men25.40.F.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.40.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.45.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.50.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.55.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.60.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.65.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.70.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.75.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.80.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.85.cl.prop.women25.40.M.15.25[2], d.MCAR.cov.90.cl.prop.women25.40.M.15.25[2], 
                  d.MCAR.cov.95.cl.prop.women25.40.M.15.25[2], d.MCAR.true.cov.100.prop.women25.40.M.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.40.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.45.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.50.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.55.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.60.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.65.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.70.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.75.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.80.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.85.cl.prop.men40.50.F.15.25[2], d.MCAR.cov.90.cl.prop.men40.50.F.15.25[2], 
                  d.MCAR.cov.95.cl.prop.men40.50.F.15.25[2], d.MCAR.true.cov.100.prop.men40.50.F.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.40.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.45.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.50.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.55.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.60.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.65.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.70.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.75.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.80.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.85.cl.prop.women40.50.M.15.25[2], d.MCAR.cov.90.cl.prop.women40.50.M.15.25[2], 
                  d.MCAR.cov.95.cl.prop.women40.50.M.15.25[2], d.MCAR.true.cov.100.prop.women40.50.M.15.25[2],
                  
                  d.MCAR.cov.35.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.40.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.45.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.50.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.55.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.60.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.65.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.70.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.75.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.80.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.85.cl.prop.men15.25.F.25.40[2], d.MCAR.cov.90.cl.prop.men15.25.F.25.40[2], 
                  d.MCAR.cov.95.cl.prop.men15.25.F.25.40[2], d.MCAR.true.cov.100.prop.men15.25.F.25.40[2],
                  
                  d.MCAR.cov.35.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.40.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.45.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.50.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.55.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.60.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.65.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.70.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.75.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.80.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.85.cl.prop.women15.25.M.25.40[2], d.MCAR.cov.90.cl.prop.women15.25.M.25.40[2], 
                  d.MCAR.cov.95.cl.prop.women15.25.M.25.40[2], d.MCAR.true.cov.100.prop.women15.25.M.25.40[2],
                  
                  d.MCAR.cov.35.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.40.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.45.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.50.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.55.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.60.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.65.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.70.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.75.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.80.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.85.cl.prop.men25.40.F.25.40[2], d.MCAR.cov.90.cl.prop.men25.40.F.25.40[2], 
                  d.MCAR.cov.95.cl.prop.men25.40.F.25.40[2], d.MCAR.true.cov.100.prop.men25.40.F.25.40[2],
                  
                  d.MCAR.cov.35.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.40.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.45.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.50.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.55.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.60.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.65.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.70.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.75.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.80.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.85.cl.prop.women25.40.M.25.40[2], d.MCAR.cov.90.cl.prop.women25.40.M.25.40[2], 
                  d.MCAR.cov.95.cl.prop.women25.40.M.25.40[2], d.MCAR.true.cov.100.prop.women25.40.M.25.40[2],
                  
                  
                  d.MCAR.cov.35.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.40.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.45.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.50.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.55.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.60.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.65.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.70.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.75.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.80.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.85.cl.prop.men40.50.F.25.40[2], d.MCAR.cov.90.cl.prop.men40.50.F.25.40[2], 
                  d.MCAR.cov.95.cl.prop.men40.50.F.25.40[2], d.MCAR.true.cov.100.prop.men40.50.F.25.40[2],
                  
                  d.MCAR.cov.35.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.40.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.45.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.50.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.55.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.60.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.65.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.70.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.75.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.80.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.85.cl.prop.women40.50.M.25.40[2], d.MCAR.cov.90.cl.prop.women40.50.M.25.40[2], 
                  d.MCAR.cov.95.cl.prop.women40.50.M.25.40[2], d.MCAR.true.cov.100.prop.women40.50.M.25.40[2],
                  
                  d.MCAR.cov.35.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.40.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.45.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.50.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.55.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.60.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.65.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.70.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.75.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.80.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.85.cl.prop.men15.25.F.40.50[2], d.MCAR.cov.90.cl.prop.men15.25.F.40.50[2], 
                  d.MCAR.cov.95.cl.prop.men15.25.F.40.50[2], d.MCAR.true.cov.100.prop.men15.25.F.40.50[2],
                  
                  d.MCAR.cov.35.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.40.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.45.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.50.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.55.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.60.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.65.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.70.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.75.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.80.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.85.cl.prop.women15.25.M.40.50[2], d.MCAR.cov.90.cl.prop.women15.25.M.40.50[2], 
                  d.MCAR.cov.95.cl.prop.women15.25.M.40.50[2], d.MCAR.true.cov.100.prop.women15.25.M.40.50[2],
                  
                  d.MCAR.cov.35.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.40.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.45.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.50.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.55.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.60.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.65.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.70.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.75.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.80.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.85.cl.prop.men25.40.F.40.50[2], d.MCAR.cov.90.cl.prop.men25.40.F.40.50[2], 
                  d.MCAR.cov.95.cl.prop.men25.40.F.40.50[2], d.MCAR.true.cov.100.prop.men25.40.F.40.50[2],
                  
                  d.MCAR.cov.35.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.40.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.45.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.50.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.55.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.60.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.65.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.70.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.75.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.80.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.85.cl.prop.women25.40.M.40.50[2], d.MCAR.cov.90.cl.prop.women25.40.M.40.50[2], 
                  d.MCAR.cov.95.cl.prop.women25.40.M.40.50[2], d.MCAR.true.cov.100.prop.women25.40.M.40.50[2],
                  
                  d.MCAR.cov.35.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.40.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.45.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.50.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.55.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.60.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.65.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.70.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.75.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.80.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.85.cl.prop.men40.50.F.40.50[2], d.MCAR.cov.90.cl.prop.men40.50.F.40.50[2], 
                  d.MCAR.cov.95.cl.prop.men40.50.F.40.50[2], d.MCAR.true.cov.100.prop.men40.50.F.40.50[2],
                  
                  d.MCAR.cov.35.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.40.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.45.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.50.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.55.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.60.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.65.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.70.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.75.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.80.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.85.cl.prop.women40.50.M.40.50[2], d.MCAR.cov.90.cl.prop.women40.50.M.40.50[2], 
                  d.MCAR.cov.95.cl.prop.women40.50.M.40.50[2], d.MCAR.true.cov.100.prop.women40.50.M.40.50[2]
),

ncol = 14,
byrow = TRUE)

props <- round(props_infer, digits = 3)


colnames(props_infer) <- c("cl.cov.35", "cl.cov.40", "cl.cov.45",
                     "cl.cov.50", "cl.cov.55", "cl.cov.60",
                     "cl.cov.65", "cl.cov.70", "cl.cov.75",
                     "cl.cov.80", "cl.cov.85", "cl.cov.90",
                     "cl.cov.95", "true.cov.100")

rownames(props_infer) <-  c("M.15.25.F.15.25", "F.15.25.M.15.25", 
                     "M.25.40.F.15.25", "F.25.40.M.15.25", 
                     "M.40.50.F.15.25", "F.40.50.M.15.25",
                     "M.15.25.F.25.40", "F.15.25.M.25.40",
                     "M.25.40.F.25.40", "F.25.40.M.25.40",
                     "M.40.50.F.25.40", "F.40.50.M.25.40",
                     "M.15.25.F.40.50", "F.15.25.M.40.50",
                     "M.25.40.F.40.50", "F.25.40.M.40.50",
                     "M.40.50.F.40.50", "F.40.50.M.40.50") 

props_infer


```

## Goodness of fit of proportions of pairings




# Age difference in pairings from transmission clusters



## Goodness of fit of statistics of ge difference in pairings from transmission clusters


